### 2018-06-08 paper/paper.tex
Initial commit

\documentclass[sigplan]{acmart}

\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain} % removes running headers

\usepackage[english]{babel}
\usepackage{url}

\begin{document}

\title{Automatic Summarization of Scientific Texts}

\author{Maria Dobko}
\affiliation{%
  \institution{Ukrainian Catholic University\\
  Faculty of Applied Sciences}
  \city{Lviv}
  \state{Ukraine}
}
\email{dobko_m@ucu.edu.ua}

\author{Oleksandr Zaytsev}
\affiliation{%
  \institution{Ukrainian Catholic University\\
  Faculty of Applied Sciences}
  \city{Lviv}
  \state{Ukraine}
}
\email{oleks@ucu.edu.ua}

\author{Yuriy Pryima}
\affiliation{%
  \institution{Ukrainian Catholic University\\
  Faculty of Applied Sciences}
  \city{Lviv}
  \state{Ukraine}
}
\email{y.pryima@ucu.edu.ua }

\begin{abstract}

In this work we overview recent advancements in the field of abstractive text summarization and discuss the use of deep learning models, especially Generative Adversarial Networks (GAN). We apply different models to our dataset of scientifix papers, acquired from arXiv, and evaluate them in terms of simplicity and performance.

\end{abstract}

\keywords{text summarization, NLP, GAN, reinforcement learning}

\maketitle

\section{Introduction}
Abstractive text summarization is ...
as opposed to extractive summarization where

\subsection{Abstractive vs Extractive summarization}

Abstractive text summarization allows us to write summaries that are almost as good as those written by humans.

Abstractive text summarization is more challenging, but it is close to what humans do.

Data-driven approach

Automatic text summarization is the task of producing a concise and fluent summary while preserving key information content and overall meaning\cite{allahyari-17}.

\subsection{The power of extractive summarization}

Though it will not be the focus of our work, extractive text summarization is dominant in this field and serves as a baseline for abstractive models. Before we move any further, we must understand what makes statistical techniques so powerful.

\subsection{Structure of the paper}

In this study we focus on abstractive text summarization. We do a brief overview of the related work that has been done in this field. Then we proceed to discussing different models for statistical and deep summarization. Then we present our dataset of scientific papers collected from arXiv and compare the performance of different models on this dataset.

\section{Problem statement}

The main hypothesis is that generative adversarial networks with reinforcement learning based generator, when applied to the problem of abstractive scientific text summarization, can provide better results than recent state-of-the-art approaches.

The model is provided with a labeled dataset.

\begin{quote}
Significant attention has been given to minimizing a penalized least squares criterion for estimating sparse solutions to large linear systems of equations. The penalty is responsible for inducing sparsity and the natural choice is the so-called $l_0$ norm. In this paper we develop a Momentumized Iterative Shrinkage Thresholding (MIST) algorithm for minimizing the resulting non-convex criterion and prove its convergence to a local minimizer. Simulations on large data sets show superior performance of the proposed method to other methods.
\end{quote}

The title of this paper is \textbf{MIST: L0 Sparse Linear Regression with Momentum}.

\section{Related work}

Allahyari et al.\cite{allahyari-17} make a survey of the most successful text summarization techniques as of July 2017.

This September Li et al. \cite{li-cohn-17} described their submission to the sentiment analysis sub-task of ?Build It, Break It: The Language Edition (BIBI)? where they successfully apply generative approach to the problem of sentiment analysis.

In their paper \textit{Generative Adversarial Network for Abstractive Text Summarization} Liu et al.\cite{liu-17} built an adversarial model that achieved competitive ROUGE scores with the state-of-the-art methods on CNN/Daily Mail dataset. They compare the performance of their approach with three methods, including the abstractive model, the pointer-generator coverage networks, and the abstractive deep reinforced model.

In contrast Zhang et al.\cite{zhang-17} don't use reinforcement learning but rather introduce TextGAN with an LSTM-based generator and kernelized discrepancy metric.

% \section{Research design and methods}

% We will be applying existing discrete GANs to the data collected from arXiv. One of the lates successful models  for scientific text summarization will be selected as our baseline.

\section{Models for text summarization}
\subsection{Statistical models}

\subsection{Deep models}

\subsubsection{LSTM}

\subsubsection{Generative adversarial networks}
Generative adversarial networks (GAN) have shown a lot of success in image generation. However until recent years they were considered inapplicable to the discrete problems of natural language processing (NLP). The latest papers introduce novel approaches to overcoming these issues by combining GANs with reinforcement learning models and lay the foundation for the whole new field of research of adversarial language processing.

Recent studies have shown that neural networks can be used for solving NLP problems. However, models that were mostly considered for this task were convolutional neural networks and recurrent neural networks.

Applying generative adversarial networks to the problems of NLP is considered to be a complicated task because GANs are only defined for real-valued data, and all NLP is based on discrete values like words, characters, or bytes.

\begin{quote}
For example, if you output an image with a pixel value of 1.0, you can change that pixel value to 1.0001 on the next step. If you output the word "penguin", you can't change that to "penguin + .001" on the next step, because there is no such word as "penguin + .001". You have to go all the way from "penguin" to "ostrich".\footnote{Ian Goodfellow's answer to the related question on Reddit: \url{https://www.reddit.com/r/MachineLearning/comments/40ldq6/generative_adversarial_networks_for_text/}}
\end{quote}

However, in their latest paper Fedus, Goodfellow, and Dai\cite{fedus-18} overcome this problem by using reinforcement learning to train the generator while the discriminator is still trained via maximum likelihood and stochastic gradient descent, and use it to fill the gaps in the text.

Li et al.\cite{li-pan-18} take a different approach...

However, this approach has not been used for abstract text summarization of scientific papers, yet.

\section{Data collection and preparation}

arXiv provides a RESTful API\footnote{\url{https://arxiv.org/help/api/index}} that allows us to search for papers from a specific category and inside a specific time range. The results are returned as an HTML page which can be easily parsed.

\paragraph{Collecting paper IDs} We started by making requests to arXiv and parsing the response to acquire unique identifiers of each paper. These are the fixed-length strings that look like this: \textbf{1801.01587}. They allow us to access everything related to this paper (including its metadata and full text as PDF). We have only collected 2000 IDs from stat.ML category. We didn't collect all the papers because of network restrictions of arXiv API, huge amount of space required to store them, and the time required to process them. We might create a larger database of papers till the second evaluations, but for now a sample of 2000 random papers from one category will be enough.

\paragraph{Collecting abstracts} Having the list of paper IDs it was no trouble to make 2000 requests to the API and collect abstracts of these papers in plain text form. To get the full text of a paper we must parse its PDF, which can introduce noise and loose peces of text. So being able to collect abstracts directly from arXiv greatly simplifies the task.

\paragraph{Downloading PDF files} The same way as we did it with abstracts, we were able to construct URLs using paper IDs, and donload each paper using wget tool.

\paragraph{Extracting text from PDF} Extracting text from PDF is a complicated task. We used a python binding to Apache Tika\footnote{\url{https://github.com/chrismattmann/tika-python}} to parse the PDF files. The extracted text contained many special characters (noise) which had to be removed manually.

\paragraph{Cleaning the text} After removing special characters produced by Tika, we also had to remove all mathematical expressions because the can not be parsed into plain text and Tika just turns an expression like this $y = f(x)$ into something like \textit{y f x} or \textit{ytx}. More complex expressions (like sums, integrals etc.) produced much more noise, and it was very hard to identify and remove it. We wanted to remove everething that is not a known English word. But that would filter out words like "GAN", "backprop" etc. So we filtered the words based on their length and frequence of vowels. That leaves some noise, but it shouldn't cause too much damage to our model (at least less damage than would be caused by removing the word "GAN"). Hopefully, we will come up with a more ellegant solution by the time of second evaluations.

\paragraph{} As a result, we have created a database of 2000 papers. For each of these papers we store its name, a list of authors, full text without an abstract, and abstract stored in a separate column.

\section{Experiments and results}
\subsection{Statistical NLP}
\subsection{Deep LSTM}
\subsection{GAN}

\section{Evaluation}

ROUGE is the most widely used metric for automatic evaluation.

\section{Baseline models}

As a baselin model we selected a seq2seq model with deep LSTM\cite{sutskever-17} together with beam search and attention. At this point it is too hard to produce an abstract from the text of a paper, so we started with a simpler task of generating a title from the text of an abstract. We represented each absract as a numeric vector using word embedings and fed it to the model together with a corresponding title. After some training our model was able to generate meaningful titles for most abstracts. Take a look at this example:

\paragraph{Abstract} this is great popcorn and i too have the whirly pop. the unk packs work wonderfully. i have not found it too salty or the packages leak. i have found the recent price of \$35 too expensive and have purchased direct from great american for half the price.

\paragraph{Predicted summary} great popcorn!!

\paragraph{Actual summary} great unk american popcorn

\paragraph{} It is not clear yet if we will be able to produce abstracts based on the whole text of an article. Such problems have very big feature space which might overcomplicate our task. So on the next stage of our project we will continue generating titles from abstracts and try doing that with discrete GANs. If our experiments prove to be successful, we will try scaling up to full texts of papers in our dataset.

% \subsection{Timeframes}

% \paragraph{Deliverables for the $1^{st}$ evaluation}
% \begin{itemize}
% \item Dataset of papers collected from arXiv
% \item Results of feature extraction
% \item Implementations of the baseline state-of-the-art model and its application to our dataset
% \end{itemize}

% \paragraph{Deliverables for the $2^{nd}$ (final) evaluation}
% \begin{itemize}
% \item Implementation of several discrete GAN models
% \item Evaluation of the created models on our dataset
% \item Paper describing the results of our research
% \end{itemize}

\section{Strength and weakness of the study}
GANs have proved to be the most successful when it comes to generative images, but their application to the problems of the text generation is not well studied. So we expect our research to introduce novel approaches and original ideas that may advance the field of natural language processing.
However, there are high risks that this approach may not give good results at all, because there are still lots of issues about  usage of neural networks with language data. The other possible weakness is a difficulty to compare the results with other papers, as there are not a lot of researches concerning this or relative subject. 
We are also currently looking for supervisors who might be interested in the following topic, so we could have a mentorship during the research.

\section*{Conclusions}

In this paper we demonstrated how Generative Adversarial Networks can be used for abstractive text summarization.

\bibliographystyle{plain}
\bibliography{paper}

\end{document}

### 2018-06-08 src/get_abstracts.py

@@ -1,0 +1,41 @@
+import os
+import numpy as np
+import pandas as pd
+import requests
+from bs4 import BeautifulSoup
+from tqdm import tqdm
+
+papers = os.listdir('papers/')
+papers = [name for name in papers if name != '.DS_Store']
+
+# Removing .pdf
+ids = [name[:-4] for name in papers]
+df = pd.DataFrame({"id": ids})
+
+def get_url(pid):
+    return 'https://arxiv.org/abs/{}'.format(pid)
+
+df['title'] = ''
+
+for i in tqdm(range(len(df))):
+    # We make too many requests and eventually will get disconnected 
+    # This condition will allow us to continue where we left
+    if df.title.iloc[i] == '':
+        pid = df.id.iloc[i]
+        purl = get_url(pid)
+
+        req = requests.get(purl)
+
+        if req.status_code == 200:
+            soup = BeautifulSoup(req.text, "lxml")
+
+            # Extract abstract
+            title = soup.find('h1', {'class': 'title'})
+
+            # Remove Title:
+            title = title.text[7:]
+
+            df.title.iloc[i] = title
+
+df.to_csv('abstracts.csv', header=True, index=False, sep="\t")
+

### 2018-06-08 paper/paper.tex
Wrote few paragraphs about the evaluation metrics

@@
 
+\section{Evaluation metrics}
+
+The most widely used score for evaluating text summarizations is Recall-Oriented Understudy for Gisting Evaluation (ROUGE) inroduced by Chin-Yew Lin in 2004\cite{lin-4}\cite{das-7}\cite{kishore-2}.
+
+\[ \text{ROUGE-N}(s) = \frac{\sum_{r \in R} \langle \Phi_n(r), \Phi_n(s) \rangle}{\sum_{r \in R} \langle \Phi_n(r), \Phi_n(r) \rangle} \]
+
+\[ \text{ROUGE-L}(s) = \frac{(1 + \beta^2) R_{LCS} P_{LCS}}{R_{LCS} + \beta^2 P_{LCS}} \]
+
+The problem with these scores is that all of them measure the number of words that occur in both expected and actual summary.
+This can be useful for extractive summarization but makes little sense for abstractive, because the summary can be generated with completely new words.
+
+For example, if the expeced summary is \textit{"The great paper"} and our model produces the summary \textit{"A wonderful article"}, ROUGE score will be $0$, even though the summary is perfect.
+
+\subsection{Embedding-based metric}
+
+We propose a metric that uses word embeddings to evaluate summaries based on their semmantic distance to the space of expected summaries.
+
+Our assumption is that a good summary of a document contains words that are semantically close to the most important words in that document.
+
+Let's denote an $n$-word summary as $S = (s_1, s_2, \dots, s_n)$ and let $c_1, c_2, \dots, c_k$ be the $k$ most important words in the document.
+We define the norm of each word in the summary as its distance to the closest important word in the document
+
+\[ ||x||_{EMB} = \operatorname*{min}_j ||s_i - c_j||_2 \]
+
+Now the norm of a whole summary is the average of the norms of it words
+
+\[ ||S||_{EMB} = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]
+
+To choose which words are important we can use an algorithm of extractive text summarization.
+We will use \textbf{term frequency-inverse document frequency} (tf-idf) as a measure of importance because of its simplicity and importance (according to \cite{kumar-16}, tf-idf is one of the universally used terminologies in extractive summarization).
+
 \section{Experiments and results}
-\subsection{Statistical NLP}
+
+We have tried different methods of text summarization, both extractive (TextRank, TF-IDF) and abstractive (LSTM, SeqGAN).
+
+\subsection{TextRank}
+
 \subsection{Deep LSTM}
@@
 
-\section{Evaluation}
+\section{Evaluating results}
 
-ROUGE is the most widely used metric for automatic evaluation.
+\begin{tabular}{|l|c|c|c|}
+\hline
+\textbf{Model} & \textbf{ROUGE-1} & \textbf{ROUGE-2} & \textbf{ROUGE-L} \\
+\hline
+TextRank & 0 & 0 & 0 \\
+LSTM & 0 & 0 & 0 \\
+SeqGAN & 0 & 0 & 0 \\
+\hline
+\end{tabular}
 
@@
 
+% \section*{Acknowledgements}
+
+% We would like to express our gratitude to Anatolii Stehnii, Artem Chernodub, Maryana Romanyshyn, and Oksana Tkach for supporting us with their advices.
+
 \bibliographystyle{plain}

### 2018-06-09 paper/paper.tex
Added a sentence about our metric to the abstract
Removed old paragraphs from the paper

@@
 
+We propose our own metric based on word-embeddings, which we believe will be more suitable for evaluation of abstractive summaries.
+
 \end{abstract}
 
-\keywords{text summarization, NLP, GAN, reinforcement learning}
+\keywords{text summarization, NLP}
 
@@
 
-\section{Problem statement}
-
-The main hypothesis is that generative adversarial networks with reinforcement learning based generator, when applied to the problem of abstractive scientific text summarization, can provide better results than recent state-of-the-art approaches.
-
-The model is provided with a labeled dataset.
-
-\begin{quote}
-Significant attention has been given to minimizing a penalized least squares criterion for estimating sparse solutions to large linear systems of equations.
-The penalty is responsible for inducing sparsity and the natural choice is the so-called $l_0$ norm.
-In this paper we develop a Momentumized Iterative Shrinkage Thresholding (MIST) algorithm for minimizing the resulting non-convex criterion and prove its convergence to a local minimizer.
-Simulations on large data sets show superior performance of the proposed method to other methods.
-\end{quote}
-
-The title of this paper is \textbf{MIST: L0 Sparse Linear Regression with Momentum}.
-
 \section{Related work}
@@
 % We will be applying existing discrete GANs to the data collected from arXiv. One of the lates successful models  for scientific text summarization will be selected as our baseline.
+
+\section{Data collection and preparation}
+
+arXiv provides a RESTful API\footnote{\url{https://arxiv.org/help/api/index}} that allows us to search for papers from a specific category and inside a specific time range.
+The results are returned as an HTML page which can be easily parsed.
+
+\paragraph{Collecting paper IDs} We started by making requests to arXiv and parsing the response to acquire unique identifiers of each paper.
+These are the fixed-length strings that look like this: \textbf{1801.01587}.
+They allow us to access everything related to this paper (including its metadata and full text as PDF).
+We have only collected 2000 IDs from stat.ML category.
+We didn't collect all the papers because of network restrictions of arXiv API, huge amount of space required to store them, and the time required to process them.
+Same approach can be used to collect more data, but for our problem a set of 2000 papers from one category is enough.
+For example, DUC (Document Understanding Conference) dataset which is among the most commonly used in the feld of text summarization has 30 sets with approximately 10 documents each\footnote{\url{https://www-nlpir.nist.gov/projects/duc/guidelines/2001.html}}.
+
+\paragraph{Collecting abstracts} Having the list of paper IDs it was no trouble to make 2000 requests to the API and collect abstracts of these papers in plain text form.
+To get the full text of a paper we must parse its PDF, which can introduce noise and loose peces of text.
+So being able to collect abstracts directly from arXiv greatly simplifies the task.
+
+\paragraph{Downloading PDF files} The same way as we did it with abstracts, we were able to construct URLs using paper IDs, and donload each paper using wget tool.
+
+\paragraph{Extracting text from PDF} Extracting text from PDF is a complicated task.
+We used a python binding to Apache Tika\footnote{\url{https://github.com/chrismattmann/tika-python}} to parse the PDF files.
+The extracted text contained many special characters (noise) which had to be removed manually.
+
+\paragraph{Cleaning the text} After removing special characters produced by Tika, we also had to remove all mathematical expressions because the can not be parsed into plain text and Tika just turns an expression like this $y = f(x)$ into something like \textit{y f x} or \textit{ytx}.
+More complex expressions (like sums, integrals etc.) produced much more noise, and it was very hard to identify and remove it.
+We wanted to remove everething that is not a known English word.
+But that would filter out words like "GAN", "backprop" etc.
+So we filtered the words based on their length and frequence of vowels.
+That leaves some noise, but it shouldn't cause too much damage to our model (at least less damage than would be caused by removing the word "GAN").
+Hopefully, we will come up with a more ellegant solution by the time of second evaluations.
+
+\paragraph{} As a result, we have created a database of 2000 papers.
+For each of these papers we store its name, a list of authors, full text without an abstract, and abstract stored in a separate column.
+
+\subsection{Examples}
+
+\begin{quote}
+Significant attention has been given to minimizing a penalized least squares criterion for estimating sparse solutions to large linear systems of equations.
+The penalty is responsible for inducing sparsity and the natural choice is the so-called $l_0$ norm.
+In this paper we develop a Momentumized Iterative Shrinkage Thresholding (MIST) algorithm for minimizing the resulting non-convex criterion and prove its convergence to a local minimizer.
+Simulations on large data sets show superior performance of the proposed method to other methods.
+\end{quote}
+
+The title of this paper is \textbf{MIST: L0 Sparse Linear Regression with Momentum}.
 
@@
 
-\section{Data collection and preparation}
+\section{Evaluation metrics}
 
-arXiv provides a RESTful API\footnote{\url{https://arxiv.org/help/api/index}} that allows us to search for papers from a specific category and inside a specific time range.
-The results are returned as an HTML page which can be easily parsed.
+Evaluating a summary is a difficult task because there does not exist an ideal summary for a given document or set of documents.
+\cite{das-7}.
+Manual evaluation is too expensive, so we will only be considering the automatic techniques.
 
-\paragraph{Collecting paper IDs} We started by making requests to arXiv and parsing the response to acquire unique identifiers of each paper.
-These are the fixed-length strings that look like this: \textbf{1801.01587}.
-They allow us to access everything related to this paper (including its metadata and full text as PDF).
-We have only collected 2000 IDs from stat.ML category.
-We didn't collect all the papers because of network restrictions of arXiv API, huge amount of space required to store them, and the time required to process them.
-We might create a larger database of papers till the second evaluations, but for now a sample of 2000 random papers from one category will be enough.
-
-\paragraph{Collecting abstracts} Having the list of paper IDs it was no trouble to make 2000 requests to the API and collect abstracts of these papers in plain text form.
-To get the full text of a paper we must parse its PDF, which can introduce noise and loose peces of text.
-So being able to collect abstracts directly from arXiv greatly simplifies the task.
-
-\paragraph{Downloading PDF files} The same way as we did it with abstracts, we were able to construct URLs using paper IDs, and donload each paper using wget tool.
-
-\paragraph{Extracting text from PDF} Extracting text from PDF is a complicated task.
-We used a python binding to Apache Tika\footnote{\url{https://github.com/chrismattmann/tika-python}} to parse the PDF files.
-The extracted text contained many special characters (noise) which had to be removed manually.
-
-\paragraph{Cleaning the text} After removing special characters produced by Tika, we also had to remove all mathematical expressions because the can not be parsed into plain text and Tika just turns an expression like this $y = f(x)$ into something like \textit{y f x} or \textit{ytx}.
-More complex expressions (like sums, integrals etc.) produced much more noise, and it was very hard to identify and remove it.
-We wanted to remove everething that is not a known English word.
-But that would filter out words like "GAN", "backprop" etc.
-So we filtered the words based on their length and frequence of vowels.
-That leaves some noise, but it shouldn't cause too much damage to our model (at least less damage than would be caused by removing the word "GAN").
-Hopefully, we will come up with a more ellegant solution by the time of second evaluations.
-
-\paragraph{} As a result, we have created a database of 2000 papers.
-For each of these papers we store its name, a list of authors, full text without an abstract, and abstract stored in a separate column.
-
-\section{Evaluation metrics}
+Automatic evaluation metrics compare manually written ideal summaries with summaries generated automatically by summarization systems.
 

### 2018-06-09 src/models/seq2seqWithAttention/summarization_model.py
add seq2seqgan

@@ -1,0 +1,766 @@
+from __future__ import division
+import numpy as np
+
+filename = 'glove.6B.50d.txt'
+def loadGloVe(filename):
+    vocab = []
+    embd = []
+    file = open(filename,'r')
+    for line in file.readlines():
+        row = line.strip().split(' ')
+        vocab.append(row[0])
+        embd.append(row[1:])
+    print('Loaded GloVe!')
+    file.close()
+    return vocab,embd
+vocab,embd = loadGloVe(filename)
+
+embedding = np.asarray(embd)
+embedding = embedding.astype(np.float32)
+
+word_vec_dim = len(embedding[0])
+#Pre-trained GloVe embedding
+
+
+# In[ ]:
+
+
+def np_nearest_neighbour(x):
+    #returns array in embedding that's most similar (in terms of cosine similarity) to x
+        
+    xdoty = np.multiply(embedding,x)
+    xdoty = np.sum(xdoty,1)
+    xlen = np.square(x)
+    xlen = np.sum(xlen,0)
+    xlen = np.sqrt(xlen)
+    ylen = np.square(embedding)
+    ylen = np.sum(ylen,1)
+    ylen = np.sqrt(ylen)
+    xlenylen = np.multiply(xlen,ylen)
+    cosine_similarities = np.divide(xdoty,xlenylen)
+
+    return embedding[np.argmax(cosine_similarities)]
+
+
+def word2vec(word):  # converts a given word into its vector representation
+    if word in vocab:
+        return embedding[vocab.index(word)]
+    else:
+        return embedding[vocab.index('unk')]
+
+def vec2word(vec):   # converts a given vector representation into the represented word 
+    for x in xrange(0, len(embedding)):
+        if np.array_equal(embedding[x],np.asarray(vec)):
+            return vocab[x]
+    return vec2word(np_nearest_neighbour(np.asarray(vec)))
+
+
+# In[ ]:
+
+
+import pickle
+
+with open ('vec_summaries', 'rb') as fp:
+    vec_summaries = pickle.load(fp)
+
+with open ('vec_texts', 'rb') as fp:
+    vec_texts = pickle.load(fp)
+    
+
+
+# In[ ]:
+
+
[…]

### 2018-06-09 src/data_collection/generate_txt_abstract.py
data collection: dataset generation, models: TextRank

@@ -1,0 +1,19 @@
+import pandas as pd
+import sys, os
+
+file_dir = '/home/maria/Documents/Courses_UCU/ML/Course_work/abstracts-2K.csv'
+directory = './abstracts_txt/'
+if not os.path.exists(directory):
+    os.makedirs(directory)
+
+all_papers = pd.read_csv(file_dir, delimiter='\t')
+
+# This representation of dataset's abstracts is needed for SeqGAN
+for i, paper in all_papers.iterrows():
+    with open(directory + paper['id'] + '.txt', "w") as f:
+        abstract = paper['abstract']
+
+        abstract = [abstract[i:i+50] for i in range(0, len(abstract), 50)]
+        f.write('\n'.join(abstract))
+
+print("Done!")

### 2018-06-09 src/data_collection/whole_paper_to_txt.py

@@ -1,0 +1,24 @@
+import pandas as pd
+import sys, os
+
+file_dir = '/home/maria/Documents/Courses_UCU/ML/Course_work/data.csv'
+directory = './texts_noabstract_txt/'
+
+if not os.path.exists(directory):
+    os.makedirs(directory)
+
+all_papers = pd.read_csv(file_dir)
+
+# This representation of dataset is needed for SeqGAN
+# Creating folder with name {directory} with txt files. Each file - parsed paper in '50 chars per row' format.
+for i, paper in all_papers.iterrows():
+    with open('./abstracts_txt/'+ paper['name'][:-4]+'.txt') as abs:
+        abstract = ' '.join(abs.read().split('\n'))
+        # print(abstract)
+    with open(directory + paper['name'][:-4] + '.txt', "w") as f:
+        text = paper['text']
+        paper = text # + abstract    # if we need both abstract and text
+        paper = [paper[i:i+50] for i in range(0, len(paper), 50)]
+        f.write('\n'.join(paper))
+
+print("Done!")

### 2018-06-09 src/models/TextRank/one_paper_summarization.py

@@ -1,0 +1,39 @@
+from gensim.summarization.summarizer import summarize
+from nltk.corpus import stopwords
+from nltk.tokenize import RegexpTokenizer
+import pandas as pd
+from nltk.translate.bleu_score import sentence_bleu
+from rouge import Rouge
+
+# Summarization of one document using TextRank-based model from gensim library and calculating BLEU & ROUGE scores
+
+
+def summarize_doc(content, len_words):
+    summarized = summarize(content,  word_count=30)
+    words = summarized.split(' ')
+    tokenizer = RegexpTokenizer(r'\w+')
+    filtered_words = [word for word in words if word not in stopwords.words('english')]
+    filtered_words = tokenizer.tokenize(' '.join(filtered_words))
+    return summarized, filtered_words
+
+dataset = pd.read_csv('./dataset.csv')
+ind = 5   # paper id, position in dataset
+content = dataset['text'][ind]
+
+num_words = len(dataset['abstract'][ind].split(' '))
+sum_text, filtered_words = summarize_doc(content, num_words)
+
+abstract = dataset['abstract'][ind].split()
+tokenizer = RegexpTokenizer(r'\w+')
+filtered_abstract = [word for word in abstract if word not in stopwords.words('english')]
+filtered_abstract = tokenizer.tokenize(' '.join(filtered_abstract))
+
+
+bleu_score = sentence_bleu(sum_text.split(' '), abstract)
+rouge = Rouge()
+rouge_score = rouge.get_scores(sum_text, ' '.join(abstract))
+
+print(bleu_score, rouge_score)
+print(dataset['abstract'][ind])
+print("\n")
+print(sum_text)

### 2018-06-09 src/models/TextRank/summarize_textrank.py

@@ -1,0 +1,79 @@
+from gensim.summarization.summarizer import summarize
+from nltk.corpus import stopwords
+from nltk.tokenize import RegexpTokenizer
+from nltk.translate.bleu_score import sentence_bleu
+from rouge import Rouge
+import pandas as pd
+
+
+def summarize_doc(content, len_words):
+    """
+    Summarization of one document using TextRank-based model from gensim library.
+    :param content: text in string format
+    :param len_words: number of words to 'generate', output summary size
+    :return: summary and list of cleaned words from summary
+    """
+    summarized = summarize(content,  word_count=len_words)
+    words = summarized.split(' ')
+    tokenizer = RegexpTokenizer(r'\w+')
+    filtered_words = [word for word in words if word not in stopwords.words('english')]
+    filtered_words = tokenizer.tokenize(' '.join(filtered_words))
+    return summarized, filtered_words
+
+dataset = pd.read_csv('./dataset.csv')
+testrank_res = pd.DataFrame(dataset['id'])
+testrank_res['BLEU'], testrank_res['ROUGE2_f'], testrank_res['ROUGE1_f'], testrank_res['ROUGE1_p'], testrank_res['ROUGE2_p'] = None, None, None, None, None
+testrank_res['BLEU_unfilter'], testrank_res['ROUGE2_f_unfilter'], testrank_res['ROUGE1_f_unfilter'], testrank_res['ROUGE1_p_unfilter'], testrank_res['ROUGE2_p_unfilter'] = None, None, None, None, None
+testrank_res['Summary'] = None
+testrank_res['ROUGEl_p_unfilter'], testrank_res['ROUGEl_p'], testrank_res['ROUGEl_f'], testrank_res['ROUGEl_f_unfilter'] = None, None, None, None
+
+for index, paper in dataset.iterrows():
+    try:
+        content = paper['text']
+        if len(content) < len(paper['abstract']) * 3:
+            print("Too small text for paper", paper['id'], index)
+            raise ValueError
+        # ratio = round(len(paper['abstract'])/len(content), 3)
+        num_words = len(paper['abstract'].split(' '))
+        sum_text, filtered_words = summarize_doc(content, num_words)
+
+        abstract = paper['abstract'].split()
+        tokenizer = RegexpTokenizer(r'\w+')
[…]

### 2018-06-09 paper/paper.tex
Cleaned up latex folder, created gitignore

@@
 
-arXiv provides a RESTful API\footnote{\url{https://arxiv.org/help/api/index}} that allows us to search for papers from a specific category and inside a specific time range.
-The results are returned as an HTML page which can be easily parsed.
+Thanks to the open policy of arXiv we were able to collect our own dataset of scientific papers from \textit{stat.ML} category.
+We publish it together with this paper an encourage everyone to use it as they like in their own projects.
 
-\paragraph{Collecting paper IDs} We started by making requests to arXiv and parsing the response to acquire unique identifiers of each paper.
-These are the fixed-length strings that look like this: \textbf{1801.01587}.
-They allow us to access everything related to this paper (including its metadata and full text as PDF).
-We have only collected 2000 IDs from stat.ML category.
-We didn't collect all the papers because of network restrictions of arXiv API, huge amount of space required to store them, and the time required to process them.
-Same approach can be used to collect more data, but for our problem a set of 2000 papers from one category is enough.
+\paragraph{Structure of the data} Each paper on arXiv has a unique identifier (for eample: 1801.01587).
+It can be used to extract any data that is available and related to that paper, including its metadata and full text as PDF.
+
+Our dataset contains 2000 documents (papers). Each one of them is represented by a row with three properties:
+
+\begin{itemize}
+  \item arXiv's unique identifier
+  \item title
+  \item abstract
+  \item body of the paper
+\end{itemize}
+
+Our script\footnote{Code and instructions for collecting the data is available in our repository: \url{https://github.com/MachineLearningUCU/TextSummarization}} can be used to collect more data, but for our problem a set of 2000 papers from one category is enough.
 For example, DUC (Document Understanding Conference) dataset which is among the most commonly used in the feld of text summarization has 30 sets with approximately 10 documents each\footnote{\url{https://www-nlpir.nist.gov/projects/duc/guidelines/2001.html}}.
 
-\paragraph{Collecting abstracts} Having the list of paper IDs it was no trouble to make 2000 requests to the API and collect abstracts of these papers in plain text form.
-To get the full text of a paper we must parse its PDF, which can introduce noise and loose peces of text.
-So being able to collect abstracts directly from arXiv greatly simplifies the task.
+\paragraph{Cleaning the text} We collected our data as PDF files and parsed them to extract the raw text.
+This produced a huge amount of uniterpretable UTF-8 characters from mathematical expressions.
+After removing those extra characters.
 
-\paragraph{Downloading PDF files} The same way as we did it with abstracts, we were able to construct URLs using paper IDs, and donload each paper using wget tool.
-
-\paragraph{Extracting text from PDF} Extracting text from PDF is a complicated task.
-We used a python binding to Apache Tika\footnote{\url{https://github.com/chrismattmann/tika-python}} to parse the PDF files.
-The extracted text contained many special characters (noise) which had to be removed manually.
-
-\paragraph{Cleaning the text} After removing special characters produced by Tika, we also had to remove all mathematical expressions because the can not be parsed into plain text and Tika just turns an expression like this $y = f(x)$ into something like \textit{y f x} or \textit{ytx}.
-More complex expressions (like sums, integrals etc.) produced much more noise, and it was very hard to identify and remove it.
-We wanted to remove everething that is not a known English word.
-But that would filter out words like "GAN", "backprop" etc.
-So we filtered the words based on their length and frequence of vowels.
-That leaves some noise, but it shouldn't cause too much damage to our model (at least less damage than would be caused by removing the word "GAN").
-Hopefully, we will come up with a more ellegant solution by the time of second evaluations.
-
-\paragraph{} As a result, we have created a database of 2000 papers.
-For each of these papers we store its name, a list of authors, full text without an abstract, and abstract stored in a separate column.
-
-\subsection{Examples}
-
-\begin{quote}
-Significant attention has been given to minimizing a penalized least squares criterion for estimating sparse solutions to large linear systems of equations.
-The penalty is responsible for inducing sparsity and the natural choice is the so-called $l_0$ norm.
-In this paper we develop a Momentumized Iterative Shrinkage Thresholding (MIST) algorithm for minimizing the resulting non-convex criterion and prove its convergence to a local minimizer.
-Simulations on large data sets show superior performance of the proposed method to other methods.
-\end{quote}
-
-The title of this paper is \textbf{MIST: L0 Sparse Linear Regression with Momentum}.
+We wanted to remove everething that is not a known English word, but that would filter out words like "GAN", "backprop" etc.
+as most standard corpuses of words, such as nltk.corpus, don't include specialized scientific terminology.
+So we filtered the words using manually created rules based on features like word length and frequence of vowels.
+This leaves some noise behind, but it will not affect our models.
 
 \section{Models for text summarization}
-\subsection{Statistical models}
-
-\subsection{Deep models}
-
-\subsubsection{LSTM}
 

### 2018-06-10 paper/paper.tex
Modified gitignore

@@
 
-Thanks to the open policy of arXiv we were able to collect our own dataset of scientific papers from \textit{stat.ML} category.
+Thanks to the open policy of arXiv we were able to collect our own dataset of scientific papers from \textit{stat.ML} category\footnote{\url{https://arxiv.org/list/stat.ML/recent}}.
 We publish it together with this paper an encourage everyone to use it as they like in their own projects.
@@
 
-Our dataset contains 2000 documents (papers). Each one of them is represented by a row with three properties:
+Our dataset contains 2000 documents (papers). Each one of them is represented by a row with the following properties:
 
@@
 
-Evaluating a summary is a difficult task because there does not exist an ideal summary for a given document or set of documents.
-\cite{das-7}.
-Manual evaluation is too expensive, so we will only be considering the automatic techniques.
+Evaluating a summary is a difficult task because there is no single summary that would be ideal for a given document.
+In most cases even human evaluators can not agree on which of the given summaries is better.\cite{das-7}.
+Unlike other NLP problems, like translation or parsing, when it comes to text summarization we can not clearly define what makes a summary good or bad.
+Manual evaluation of summaries is too expensive, so in the following sections we will only consider automatic techniques.
 
 Automatic evaluation metrics compare manually written ideal summaries with summaries generated automatically by summarization systems.
+
+\subsection{ROUGE}
 

### 2018-06-10 paper/paper.tex
Wrote about the assumptions we make when evaluating summaries

@@
 
-\begin{itemize}
+\begin{enumerate}
   \item arXiv's unique identifier
@@
   \item body of the paper
-\end{itemize}
+\end{enumerate}
 
@@
 
-Evaluating a summary is a difficult task because there is no single summary that would be ideal for a given document.
-In most cases even human evaluators can not agree on which of the given summaries is better.\cite{das-7}.
-Unlike other NLP problems, like translation or parsing, when it comes to text summarization we can not clearly define what makes a summary good or bad.
-Manual evaluation of summaries is too expensive, so in the following sections we will only consider automatic techniques.
+Evaluating a summary is a difficult task because there is no such thing as a single summary that would be ideal for a given document.
+In most cases even human evaluators can not agree on which of the given summaries is better\cite{das-7}.
+Unlike other NLP problems, such as translation or parsing, when it comes to text summarization we can not clearly define what makes a summary good or bad.
+Therefore we must make assumptions about the space of good summaries.
 
-Automatic evaluation metrics compare manually written ideal summaries with summaries generated automatically by summarization systems.
+\begin{enumerate}
+\item assume that a good summary would be close to some \textit{ideal} summary manually created by humans
+\item assume that the goodness of summary can be measured as the ammount of important information it contains (this assumption can be infered from the definition of text summarization).
+\end{enumerate}
+
+In the following sections we briefly describe some of the commonly used metrics for text summarization that is based on the first assumption and propose our own metric that is based on second one (in fact, we will show that the proposed metric can be formulated in a different way to work with the first assumption).
 

### 2018-06-10 paper/paper.tex
Updated the section about metrics

@@
 
-The most widely used score for evaluating text summarizations is Recall-Oriented Understudy for Gisting Evaluation (ROUGE) inroduced by Chin-Yew Lin in 2004\cite{lin-4}\cite{das-7}\cite{kishore-2}.
+The most widely used score for evaluating text summarizations is ROUGE (Recall-Oriented Understudy for Gisting Evaluation) inroduced by Chin-Yew Lin in 2004\cite{lin-4}\cite{kishore-2}.
 
@@
 
-The problem with these scores is that all of them measure the number of words that occur in both expected and actual summary.
-This can be useful for extractive summarization but makes little sense for abstractive, because the summary can be generated with completely new words.
+ROUGE works well for extractive text summarization.
+But if we need to evaluate the generated summary which contains different words from the ones that occured in paper, the score will always be small because, even though the new words can be close to the expected ones, two summaries don't overlap in terms of word equality.
 
-For example, if the expeced summary is \textit{"The great paper"} and our model produces the summary \textit{"A wonderful article"}, ROUGE score will be $0$, even though the summary is perfect.
+For example, if the human-created summary is \textit{"The great paper"} and our model produces \textit{"A wonderful article"}, ROUGE score will be $0$, even though the summary is perfect.
 
@@
 
-We propose a metric that uses word embeddings to evaluate summaries based on their semmantic distance to the space of expected summaries.
+We propose a metric that uses word embeddings to evaluate summaries based on their semmantic distance to the space of good summaries.
+Our assumption is that a good summary of a document contains words that are semantically close to the most important words or n-grams in that document.
 
-Our assumption is that a good summary of a document contains words that are semantically close to the most important words in that document.
+Let's denote an $n$-word summary as $S = (s_1, s_2, \dots, s_n)$ and let $c_1, c_2, \dots, c_k$ be the $k$ most important n-grams in the document.
+For each n-gram in the generated summary we calculate the embedding-based score as its distance to the closest important n-gram in the document.
 
-Let's denote an $n$-word summary as $S = (s_1, s_2, \dots, s_n)$ and let $c_1, c_2, \dots, c_k$ be the $k$ most important words in the document.
-We define the norm of each word in the summary as its distance to the closest important word in the document
+\[ \text{EBM-N}(s_i) = \operatorname*{min}_j ||s_i - c_j||_2 \]
 
-\[ ||x||_{EMB} = \operatorname*{min}_j ||s_i - c_j||_2 \]
+Now we define the score of the whole summary as the average score of its words
 
-Now the norm of a whole summary is the average of the norms of it words
+\[ \text{EBM-N}(S) = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]
 
-\[ ||S||_{EMB} = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]
+This metric is in fact the continuous version of ROUGE-N.
+Instead of testing the equality of n-grams in the compared summaries we use the continuous measure of semmantic distance between those n-grams.
 
+\subsubsection{Measuring word importance}
 To choose which words are important we can use an algorithm of extractive text summarization.

### 2018-06-10 paper/paper.tex
Add seq2seq model description

--- 2018-06-10 paper/paper.tex
@@
 \documentclass[sigplan]{acmart}
-
 \settopmatter{printacmref=false} % Removes citation information below abstract
@@
 
-We have tried different methods of text summarization, both extractive (TextRank, TF-IDF) and abstractive (LSTM, SeqGAN).
+We have tried different methods of text summarization, both extractive (TextRank, TF-IDF) and abstractive (Seq2Seq, SeqGAN).
 
 \subsection{TextRank}
-
-\subsection{Deep LSTM}
-\subsection{GAN}
+\subsection{Seq2Seq}
+We have used seq2seq model with attention for a task of text summarization. Seq2seq have proven to provide state-of-art result in tasks of sequence generation.
+As input model takes paper abstract converted to the vectorized representation using word embeddings.
+The input sequence is limited by 600 words.
+All abstracts that are bigger than limit are omitted.
+All smaller abstracts are padded with $\langle\text{SOS}\rangle$ word that represents the end of a sequence.
+Model outputs sequence derived from the probability distribution.
+Each output word samples from this distribution having input sequence and previously generated samples.
+Output sequence is limited by 30 words.
+First $\langle\text{SOS}\rangle$ word represent the end of a generated summary.
 

### 2018-06-10 paper/paper.tex

@@
 \section{Models for text summarization}
+
+Three main classes of models that are used for text summarization task are statistical frequency computation models (TFIDF etc.), graph methods (TextRank, LexRank etc.) and machine learning approach.
+Statistical methods assume that the importance of a word/sentence in a text depends on the number of times the word/sentence appears in the document.
+This means that this classical approach ignores context and lexical features of the text.
+Furthermore, they are able to perform only extractive summarization.
+Graph models find similarity between words/sentences in the whole text, which is used as weight of the graph edge.
+While proving to have better results than simple frequency-based methods, they are still bounded by the absence of lexic understanding and ability to  perform extractive summary only.
+In the last years, lots of attention was focused on learning how to apply neural networks to NLP tasks, including text summarization.
+Using encoder-decoder models it is now possible to produce abstract summaries.
+In [https://arxiv.org/pdf/1602.06023.pdf] the off-the-shelf attentional encoder-decoder RNN that was originally developed for machine translation was applied to summarization and outperformed state of-the-art systems on two different English corpora.
+However, there is not much of information about neural networks usage in scientific text summarization.
 

### 2018-06-10 paper/paper.tex
Added paragraphs to medels section

@@
 Three main classes of models that are used for text summarization task are statistical frequency computation models (TFIDF etc.), graph methods (TextRank, LexRank etc.) and machine learning approach.
-Statistical methods assume that the importance of a word/sentence in a text depends on the number of times the word/sentence appears in the document.
+
+\paragraph{Statistical methods} assume that the importance of a word or sentence in a text depends on the number of times the word/sentence appears in the document.
 This means that this classical approach ignores context and lexical features of the text.
 Furthermore, they are able to perform only extractive summarization.
-Graph models find similarity between words/sentences in the whole text, which is used as weight of the graph edge.
+
+\paragraph{Graph models} find similarity between words/sentences in the whole text, which is used as weight of the graph edge.
 While proving to have better results than simple frequency-based methods, they are still bounded by the absence of lexic understanding and ability to  perform extractive summary only.
-In the last years, lots of attention was focused on learning how to apply neural networks to NLP tasks, including text summarization.
+
+\paragraph{Machine learning approach} In the last years, lots of attention was focused on learning how to apply neural networks to NLP tasks, including text summarization.
 Using encoder-decoder models it is now possible to produce abstract summaries.

### 2018-06-10 paper/paper.tex
Edited the models section

--- 2018-06-10 paper/paper.tex
@@
 \section{Models for text summarization}
+
+Three main classes of models that are used for text summarization task are statistical frequency computation models (TFIDF etc.), graph methods (TextRank, LexRank etc.) and machine learning approach.
+
+\subsection{Statistical methods}
+
+These methods are based on the assumption that the importance of a word or sentence in a text depends on the total number of times it appears in the document.
+This means that this classical approach ignores context and lexical features of the text.
+Furthermore, they are able to perform only extractive summarization.
+
+\subsection{Graph models}
+
+We can build a graph of each document where words or sentences are nodes and the edges are the connections between each pair of nodes.
+The weights on these edges represent similarity between words or sentences in the whole text.
+While proving to have better results than simple frequency-based methods, graph models are still bounded by the absence of lexic understanding and ability to perform extractive summary only.
+
+\subsection{Machine learning approach}
+
+In the last years, lots of attention was focused on learning how to apply neural networks to NLP tasks, including text summarization.
+Using encoder-decoder models it is now possible to produce abstract summaries.
+In \cite{nallapati-16} the off-the-shelf attentional encoder-decoder RNN that was originally developed for machine translation was applied to summarization and outperformed state of-the-art systems on two different English corpora.
+However, there is not much of information about neural networks usage in scientific text summarization.
 

### 2018-06-10 paper/paper.tex
Updated the metric section

@@
 
-Let's denote an $n$-word summary as $S = (s_1, s_2, \dots, s_n)$ and let $c_1, c_2, \dots, c_k$ be the $k$ most important n-grams in the document.
-For each n-gram in the generated summary we calculate the embedding-based score as its distance to the closest important n-gram in the document.
+Let $s$ be the generated summary.
+If $|s|$ is the number of words in summary $s$, then $m=|s|-n+1$ is the number of $n$-grams in this summary.
+Let $s_1, s_2, \dots, s_m$ be all $n$-grams of summary $s$ and let $c_1, c_2, \dots, c_k$ be the $k$ most important $n$-grams in the document.
+As we will show in section \ref{sec:importance}, there are many ways of measuring the importance of $n$-grams in a document.
+
+The metric we propose is in fact a continuous version of ROUGE-N.
+Instead of testing the equality of n-grams in the compared summaries we use the continuous measure of semmantic distance between those n-grams.
+
+For each $n$-gram in the generated summary we calculate the embedding-based score as its distance to the closest important $n$-gram in the document.
 
@@
 
-This metric is in fact the continuous version of ROUGE-N.
-Instead of testing the equality of n-grams in the compared summaries we use the continuous measure of semmantic distance between those n-grams.
+\subsubsection{Measuring word importance}
+\label{sec:importance}
 
-\subsubsection{Measuring word importance}
 To choose which words are important we can use an algorithm of extractive text summarization.

### 2018-06-10 paper/paper.tex
Renamed EBM to CROUGE
Renamed CROUGE to CAROUGE

@@
 
-For each $n$-gram in the generated summary we calculate the embedding-based score as its distance to the closest important $n$-gram in the document.
+For each $n$-gram in the generated summary we calculate the embedding-based score as its distance to the closest important $n$-gram in the document\footnote{CAROUGE stands for Continuous Abstractive ROUGE.
+The French word \textbf{carouge} means blackbird}.
 
-\[ \text{EBM-N}(s_i) = \operatorname*{min}_j ||s_i - c_j||_2 \]
+\[ \text{CAROUGE-N}(s_i) = \operatorname*{min}_j ||s_i - c_j||_2 \]
 
@@
 
-\[ \text{EBM-N}(S) = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]
+\[ \text{CAROUGE-N}(S) = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]
 

### 2018-06-10 paper/paper.tex
Updated the metrics section
Add GAN model description

--- 2018-06-10 paper/paper.tex
@@
 Using encoder-decoder models it is now possible to produce abstract summaries.
-In \cite{nallapati-16} the off-the-shelf attentional encoder-decoder RNN that was originally developed for machine translation was applied to summarization and outperformed state of-the-art systems on two different English corpora.
-However, there is not much of information about neural networks usage in scientific text summarization.
+In \cite{nallapati-16} the off-the-shelf attentional encoder-decoder RNN that was originally developed for machine translation was applied to summarization and outperformed state-of-the-art systems on two different English corpora.
+However, there is not much information about neural networks usage in scientific text summarization.
 
-\subsubsection{Generative adversarial networks}
-Generative adversarial networks (GAN) have shown a lot of success in image generation.
-However until recent years they were considered inapplicable to the discrete problems of natural language processing (NLP).
-The latest papers introduce novel approaches to overcoming these issues by combining GANs with reinforcement learning models and lay the foundation for the whole new field of research of adversarial language processing.
+Generative adversarial networks (GAN) are another promising approach for text summarization.
+Until recent years they were considered inapplicable to the discrete problems of natural language processing (NLP).
+The latest papers introduce novel approaches to overcoming these issues by combining GANs with reinforcement learning.
 
-Recent studies have shown that neural networks can be used for solving NLP problems.
-However, models that were mostly considered for this task were convolutional neural networks and recurrent neural networks.
-
-Applying generative adversarial networks to the problems of NLP is considered to be a complicated task because GANs are only defined for real-valued data, and all NLP is based on discrete values like words, characters, or bytes.
-
-\begin{quote}
-For example, if you output an image with a pixel value of 1.0, you can change that pixel value to 1.0001 on the next step.
-If you output the word "penguin", you can't change that to "penguin + .001" on the next step, because there is no such word as "penguin + .001".
-You have to go all the way from "penguin" to "ostrich".\footnote{Ian Goodfellow's answer to the related question on Reddit: \url{https://www.reddit.com/r/MachineLearning/comments/40ldq6/generative_adversarial_networks_for_text/}}
-\end{quote}
+Applying generative adversarial networks to the problems of NLP is considered to be a complicated task because GANs are only defined for continuous data, and all NLP is based on discrete values like words, characters, or bytes.
 
 However, in their latest paper Fedus, Goodfellow, and Dai\cite{fedus-18} overcome this problem by using reinforcement learning to train the generator while the discriminator is still trained via maximum likelihood and stochastic gradient descent, and use it to fill the gaps in the text.
-
-Li et al.\cite{li-pan-18} take a different approach...
-
-However, this approach has not been used for abstract text summarization of scientific papers, yet.
 

### 2018-06-10 paper/paper.tex

@@
 \section{Evaluation metrics}
+\label{sec:evaluation}
 
@@
 
-Let's denote an $n$-word summary as $S = (s_1, s_2, \dots, s_n)$ and let $c_1, c_2, \dots, c_k$ be the $k$ most important n-grams in the document.
-For each n-gram in the generated summary we calculate the embedding-based score as its distance to the closest important n-gram in the document.
+Let $s$ be the generated summary.
+If $|s|$ is the number of words in summary $s$, then $m=|s|-n+1$ is the number of $n$-grams in this summary.
+Let $s_1, s_2, \dots, s_m$ be all $n$-grams of summary $s$ and let $c_1, c_2, \dots, c_k$ be the $k$ most important $n$-grams in the document.
+As we will show in section \ref{sec:importance}, there are many ways of measuring the importance of $n$-grams in a document.
+The definition of $n$-gram importance is closely related to the two base assumptions that were mentioned at the beginning of section \ref{sec:evaluation}.
 
-\[ \text{EBM-N}(s_i) = \operatorname*{min}_j ||s_i - c_j||_2 \]
+The metric we propose is in fact a continuous version of ROUGE-N.
+Instead of testing the equality of n-grams in the compared summaries we use the continuous measure of semmantic distance between those n-grams.
+
+For each $n$-gram in the generated summary we calculate the embedding-based score as its distance to the closest important $n$-gram in the document\footnote{CAROUGE stands for Continuous Abstractive ROUGE.
+The French word \textbf{carouge} means blackbird}.
+
+\[ \text{CAROUGE-N}(s_i) = \operatorname*{min}_j ||s_i - c_j||_2 \]
 
@@
 
-\[ \text{EBM-N}(S) = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]
-
-This metric is in fact the continuous version of ROUGE-N.
-Instead of testing the equality of n-grams in the compared summaries we use the continuous measure of semmantic distance between those n-grams.
+\[ \text{CAROUGE-N}(s) = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]
 
 \subsubsection{Measuring word importance}
+\label{sec:importance}
+
 To choose which words are important we can use an algorithm of extractive text summarization.

### 2018-06-10 paper/paper.tex
Created a table with an example of generated abstract

--- 2018-06-10 paper/paper.tex
@@
 \usepackage{url}
+\usepackage{makecell}
 
@@
 
-% \section{Research design and methods}
-
-% We will be applying existing discrete GANs to the data collected from arXiv. One of the lates successful models  for scientific text summarization will be selected as our baseline.
-
 \section{Data collection and preparation}
@@
 As we will show in section \ref{sec:importance}, there are many ways of measuring the importance of $n$-grams in a document.
+The definition of $n$-gram importance is closely related to the two base assumptions that were mentioned at the beginning of section \ref{sec:evaluation}.
 
@@
 
-\[ \text{CAROUGE-N}(S) = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]
+\[ \text{CAROUGE-N}(s) = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]
 
@@
 \subsection{TextRank}
+In this research we used a basic model TextRank as a baseline for comparison.
+This is a graph method, influenced by PageRank algorithm, that represents the documents as a connected graph.
+We trained TextRank separately for each body of the paper and produced an extractive abstract-length summary.
+Scores were calculated on the basis of ROUGE score.
+
+\begin{table}[H]
+\caption{Example of an abstract generated by our model}
+
+\begin{center}
+\begin{tabular}{|p{0.25\linewidth}|p{0.67\linewidth}|}
+\hline
+\textbf{Title} & Churn Prediction in Mobile Social Games: Towards a Complete Assessment Using Survival Ensembles \\
+\hline
+\textbf{Real abstract} & ...for each player, we predict the probability of churning as function of time, which permits to distinguish various levels of loyalty profiles ...
+Our results show that churn prediction by survival ensembles significantly improves the accuracy and robustness of traditional analyses, like Cox regression...
+\\
+\hline
+\textbf{\makecell[l]{Generated \\ abstract}} & Conditional inference survival ensembles are constructed based on unbiased trees avoiding this problem the resulting prediction of this model contains for each player a survival function indicating the probability of churn as a function of time since the registration in the game.
+\\
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+
 \subsection{Seq2Seq}
@@
 
+\begin{table}[H]
+\caption{Evaluating different models with ROUGE}
+
+\begin{center}
 \begin{tabular}{|l|c|c|c|}
@@
 \hline
-TextRank & 0 & 0 & 0 \\
+TextRank & 18.04 & 4.10 & 10.89 \\
 LSTM & 0 & 0 & 0 \\
@@
 \end{tabular}
+\end{center}
+\end{table}
 
@@
 
-% \subsection{Timeframes}
-
-% \paragraph{Deliverables for the $1^{st}$ evaluation}
-% \begin{itemize}
-% \item Dataset of papers collected from arXiv
-% \item Results of feature extraction
-% \item Implementations of the baseline state-of-the-art model and its application to our dataset
-% \end{itemize}
-
-% \paragraph{Deliverables for the $2^{nd}$ (final) evaluation}
-% \begin{itemize}
-% \item Implementation of several discrete GAN models
-% \item Evaluation of the created models on our dataset
-% \item Paper describing the results of our research
-% \end{itemize}
-
 \section{Strength and weakness of the study}

### 2018-06-10 paper/paper.tex

--- 2018-06-10 paper/paper.tex
@@
 In contrast Zhang et al.\cite{zhang-17} don't use reinforcement learning but rather introduce TextGAN with an LSTM-based generator and kernelized discrepancy metric.
-
-% \section{Research design and methods}
-
-% We will be applying existing discrete GANs to the data collected from arXiv. One of the lates successful models  for scientific text summarization will be selected as our baseline.
 

### 2018-06-10 paper/paper.tex
Removed baseline. Updated seq2seq description

--- 2018-06-10 paper/paper.tex
@@
 \section{Evaluation metrics}
-\label{sec:evaluation}
 
@@
 
-Let $s$ be the generated summary.
-If $|s|$ is the number of words in summary $s$, then $m=|s|-n+1$ is the number of $n$-grams in this summary.
-Let $s_1, s_2, \dots, s_m$ be all $n$-grams of summary $s$ and let $c_1, c_2, \dots, c_k$ be the $k$ most important $n$-grams in the document.
-As we will show in section \ref{sec:importance}, there are many ways of measuring the importance of $n$-grams in a document.
-The definition of $n$-gram importance is closely related to the two base assumptions that were mentioned at the beginning of section \ref{sec:evaluation}.
+Let's denote an $n$-word summary as $S = (s_1, s_2, \dots, s_n)$ and let $c_1, c_2, \dots, c_k$ be the $k$ most important n-grams in the document.
+For each n-gram in the generated summary we calculate the embedding-based score as its distance to the closest important n-gram in the document.
 
-The metric we propose is in fact a continuous version of ROUGE-N.
-Instead of testing the equality of n-grams in the compared summaries we use the continuous measure of semmantic distance between those n-grams.
-
-For each $n$-gram in the generated summary we calculate the embedding-based score as its distance to the closest important $n$-gram in the document\footnote{CAROUGE stands for Continuous Abstractive ROUGE.
-The French word \textbf{carouge} means blackbird}.
-
-\[ \text{CAROUGE-N}(s_i) = \operatorname*{min}_j ||s_i - c_j||_2 \]
+\[ \text{EBM-N}(s_i) = \operatorname*{min}_j ||s_i - c_j||_2 \]
 
@@
 
-\[ \text{CAROUGE-N}(s) = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]
+\[ \text{EBM-N}(S) = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]
+
+This metric is in fact the continuous version of ROUGE-N.
+Instead of testing the equality of n-grams in the compared summaries we use the continuous measure of semmantic distance between those n-grams.
 
 \subsubsection{Measuring word importance}
-\label{sec:importance}
-
 To choose which words are important we can use an algorithm of extractive text summarization.
@@
 \subsection{Seq2Seq}
-We have used seq2seq model with attention for a task of text summarization. Seq2seq have proven to provide state-of-art result in tasks of sequence generation.
+We have used deep LSTM seq2seq model with attention for a task of text summarization.
+Seq2seq have proven to provide state-of-art result in tasks of sequence generation.
+At this point it is too hard to produce an abstract from the text of a paper, so we started with a simpler task of generating a title from the text of an abstract
 As input model takes paper abstract converted to the vectorized representation using word embeddings.
@@
 \end{tabular}
-
-\section{Baseline models}
-
-As a baselin model we selected a seq2seq model with deep LSTM\cite{sutskever-17} together with beam search and attention.
-At this point it is too hard to produce an abstract from the text of a paper, so we started with a simpler task of generating a title from the text of an abstract.
-We represented each absract as a numeric vector using word embedings and fed it to the model together with a corresponding title.
-After some training our model was able to generate meaningful titles for most abstracts.
-Take a look at this example:
-
-\paragraph{Abstract} this is great popcorn and i too have the whirly pop.
-the unk packs work wonderfully.
-i have not found it too salty or the packages leak.
-i have found the recent price of \$35 too expensive and have purchased direct from great american for half the price.
-
-\paragraph{Predicted summary} great popcorn!!
-
-\paragraph{Actual summary} great unk american popcorn
-
-\paragraph{} It is not clear yet if we will be able to produce abstracts based on the whole text of an article.
-Such problems have very big feature space which might overcomplicate our task.
-So on the next stage of our project we will continue generating titles from abstracts and try doing that with discrete GANs.
-If our experiments prove to be successful, we will try scaling up to full texts of papers in our dataset.
 

### 2018-06-10 paper/paper.tex

@@
 
-\section{Strength and weakness of the study}
-GANs have proved to be the most successful when it comes to generative images, but their application to the problems of the text generation is not well studied.
-So we expect our research to introduce novel approaches and original ideas that may advance the field of natural language processing.
-However, there are high risks that this approach may not give good results at all, because there are still lots of issues about  usage of neural networks with language data.
-The other possible weakness is a difficulty to compare the results with other papers, as there are not a lot of researches concerning this or relative subject.
-We are also currently looking for supervisors who might be interested in the following topic, so we could have a mentorship during the research.
-
 \section*{Conclusions}

### 2018-06-10 paper/paper.tex
Changed the URL of our repository

--- 2018-06-10 paper/paper.tex
@@
 
-Our script\footnote{Code and instructions for collecting the data is available in our repository: \url{https://github.com/MachineLearningUCU/TextSummarization}} can be used to collect more data, but for our problem a set of 2000 papers from one category is enough.
+Our script\footnote{Code and instructions for collecting the data is available in our repository: \url{https://github.com/Carouge/TextSummarization}} can be used to collect more data, but for our problem a set of 2000 papers from one category is enough.
 For example, DUC (Document Understanding Conference) dataset which is among the most commonly used in the feld of text summarization has 30 sets with approximately 10 documents each\footnote{\url{https://www-nlpir.nist.gov/projects/duc/guidelines/2001.html}}.

### 2018-06-10 paper/paper.tex
Add seq2seq output example

@@
 
+After some training our model was able to generate meaningful titles for most abstracts. Take a look at this example:
+
+\paragraph{Abstract} this is great popcorn and i too have the whirly pop.
+the unk packs work wonderfully.
+i have not found it too salty or the packages leak.
+i have found the recent price of \$35 too expensive and have purchased direct from great american for half the price.
+
+\paragraph{Predicted summary} great popcorn!!
+
+\paragraph{Actual summary} great unk american popcorn
+
 \section{Evaluating results}

### 2018-06-10 src/models/seq2seqWithAttention/summarization_model.py
Added acknowledgments

@@ -1,4 +1,5 @@
 """
+This model on based on the work of Jishnu Ray Chowdhury
 Source: https://github.com/JRC1995/Abstractive-Summarization
 """
 from __future__ import division

### 2018-06-10 paper/paper.tex
Added TextRank refference

--- 2018-06-10 paper/paper.tex
@@
 
-\keywords{text summarization, NLP}
+\keywords{scientific text summarization, ROUGE, seq2seq, NLP, word embeddings}
 
@@
 \section{Introduction}
-Abstractive text summarization is ...
-as opposed to extractive summarization where
+Text summarization is a problem of
 
@@
 In this research we used a basic model TextRank as a baseline for comparison.
-This is a graph method, influenced by PageRank algorithm, that represents the documents as a connected graph.
+This is a graph method, influenced by PageRank algorithm, that represents the documents as a connected graph\cite{mihalcea-4}.
 We trained TextRank separately for each body of the paper and produced an extractive abstract-length summary.

### 2018-06-10 src/models/seqgan-text-tensorflow/sample.py
Added acknowledgments

@@ -1,4 +1,8 @@
 #!/usr/bin/env python
+"""
+This model on based on the work of Benjamin Bolte
+Source: https://github.com/carrotflakes/seqgan-text-tensorflow
+"""
 """Samples from a trained model.
 
 usage: sample.py [-h] [-t DICTIONARY] [-d LOGDIR] [-c] N

### 2018-06-10 src/models/seqgan-text-tensorflow/train.py

@@ -1,4 +1,8 @@
 #!/usr/bin/env python
+"""
+This model on based on the work of Benjamin Bolte
+Source: https://github.com/carrotflakes/seqgan-text-tensorflow
+"""
 """Trains the model on some data, and saves it locally.
 
 The default training text is the `lorem.txt` file, which consists of some

### 2018-06-10 src/models/seqgan-text-tensorflow/utils.py

@@ -1,3 +1,7 @@
+"""
+This model on based on the work of Benjamin Bolte
+Source: https://github.com/carrotflakes/seqgan-text-tensorflow
+"""
 """Some utils to help with text parsing / feeding to the model."""
 
 from __future__ import division

### 2018-06-10 src/models/seqgan-text-tensorflow/utils2.py

@@ -1,3 +1,8 @@
+"""
+This model on based on the work of Benjamin Bolte
+Source: https://github.com/carrotflakes/seqgan-text-tensorflow
+"""
+
 """Some utils to help with text parsing / feeding to the model."""
 
 from __future__ import division

### 2018-06-10 src/models/RAKE/one_paper_summarization.py
RAKE model added

@@ -1,0 +1,37 @@
+from rake_nltk import Rake
+from nltk.corpus import stopwords
+from nltk.tokenize import RegexpTokenizer
+import pandas as pd
+from nltk.translate.bleu_score import sentence_bleu
+from rouge import Rouge
+
+# Rapid Automatic Keyword Extraction algorithm
+# Summarization of one document using RAKE and calculating BLEU & ROUGE scores
+
+
+def summarize_doc(content, length):
+    r = Rake()
+    r.extract_keywords_from_text(content)
+    # summarized = r.get_ranked_phrases_with_scores()
+    summarized = ' '.join(r.get_ranked_phrases()).split(' ')[:length]
+    return summarized
+
+
+dataset = pd.read_csv('../../../data/papers-2K.csv')
+ind = 9   # paper id, position in dataset
+content = dataset['text'][ind]
+abstract = dataset['abstract'][ind].split()
+
+sum_text = summarize_doc(content, len(abstract))
+
+print(len(sum_text))
+print(len(abstract))
+
+bleu_score = sentence_bleu(sum_text, abstract)
+rouge = Rouge()
+rouge_score = rouge.get_scores(' '.join(sum_text), ' '.join(abstract))
+
+print(bleu_score, rouge_score)
+print(dataset['abstract'][ind])
+print("\n")
+print(" ".join(sum_text))

### 2018-06-10 src/models/RAKE/one_paper_summarization.py
RAKE model added

@@ -1,6 +1,4 @@
 from rake_nltk import Rake
-from nltk.corpus import stopwords
-from nltk.tokenize import RegexpTokenizer
 import pandas as pd
 from nltk.translate.bleu_score import sentence_bleu
 from rouge import Rouge

### 2018-06-10 src/models/seqgan-text-tensorflow/model.py
added source to model.py

@@ -1,5 +1,8 @@
 """Utils for the TensorFlow model."""
-
+""" 
+This model on based on the work of Benjamin Bolte
+Source: https://github.com/carrotflakes/seqgan-text-tensorflow
+"""
 from collections import OrderedDict
 import warnings
 

### 2018-06-10 src/models/carouge.py
Add carouge score

@@ -1,0 +1,52 @@
+from __future__ import division
+import numpy as np
+from nltk.tokenize import RegexpTokenizer
+import scipy 
+
+filename = 'glove.6B.50d.txt'
+def loadGloVe(filename):
+    vocab = []
+    embd = []
+    file = open(filename,'r')
+    for line in file.readlines():
+        row = line.strip().split(' ')
+        vocab.append(row[0])
+        embd.append(row[1:])
+    print('Loaded GloVe!')
+    file.close()
+    return vocab,embd
+vocab, embd = loadGloVe(filename)
+
+embedding = np.asarray(embd)
+embedding = embedding.astype(np.float32)
+
+def word2vec(word):
+    if word in vocab:
+        return embedding[vocab.index(word)]
+    else:
+        return embedding[vocab.index('unk')]
+
+cosine_distance_max = 2
+
+def word_distance_normalized(vec1, vec2):
+    return scipy.spatial.distance.cosine(vec1, vec2)/cosine_distance_max
+
+def carouge(summary_generated, summary_actual):
+    tokenizer = RegexpTokenizer(r'\w+')
+    tokenized_summary_generated = tokenizer.tokenize(summary_generated)
+    tokenized_summary_actual = tokenizer.tokenize(summary_actual)
+    summary_generated_embeddings = [word2vec(word) for word in  tokenized_summary_generated ]
+    summary_actual_embeddings = [word2vec(word) for word in  tokenized_summary_actual ]
+
+
+    score = np.sum([ 
+                        1 - np.min([
+                                word_distance_normalized(act_word_emb, gen_word_emb)
+                                for  act_word_emb in summary_actual_embeddings
+                            ]) 
+
+                        for gen_word_emb in summary_generated_embeddings
+                   ])
+
+    return score/len(summary_actual_embeddings)
+

### 2018-06-10 paper/paper.tex
Uploading the updated paper

@@
 \section{Introduction}
-Text summarization is a problem of
-
-\subsection{Abstractive vs Extractive summarization}
-
-Abstractive text summarization allows us to write summaries that are almost as good as those written by humans.
-
-Abstractive text summarization is more challenging, but it is close to what humans do.
-
-Data-driven approach
 
@@
 
-\subsection{The power of extractive summarization}
+\subsection{Abstractive vs extractive summarization}
 
-Though it will not be the focus of our work, extractive text summarization is dominant in this field and serves as a baseline for abstractive models.
-Before we move any further, we must understand what makes statistical techniques so powerful.
+\paragraph{Extractive text summarization}
+
+\subsection{Abstractive summarization}
+
+\paragraph{Abstractive text summarization} allows us to write summaries that are almost as good as those written by humans.
+It is closer to what humans do when they write text summaries, but also more complex.
+T
+
+\subsection{Scientific text summarization}
+
+The problem of summarizing scientific texts is very different from general-purpose text summarization.
+Every scientific paper starts with an abstract, which by its nature is the summary of a document created by its human-author.
+This allows us to can create a human-labeled dataset of scientific papers just by separating abstracts from the text body.
 
@@
 \section{Data collection and preparation}
+\label{sec:data}
 
@@
 \subsection{ROUGE}
+\label{sec:rouge}
 
-The most widely used score for evaluating text summarizations is ROUGE (Recall-Oriented Understudy for Gisting Evaluation) inroduced by Chin-Yew Lin in 2004\cite{lin-4}\cite{kishore-2}.
+The most widely used score for evaluating text summarizations is ROUGE (Recall-Oriented Understudy for Gisting Evaluation) inroduced by Chin-Yew Lin in 2004\cite{lin-4}.
 
@@
 
-\subsection{Embedding-based metric}
+\subsection{CAROUGE}
 
@@
 
-\[ \text{CAROUGE-N}(s_i) = \operatorname*{min}_j ||s_i - c_j||_2 \]
+\[ \text{CAROUGE-N}(s_i) = \frac{1 - \operatorname*{min}_j ||s_i - c_j||}{k} \]
 
@@
 
-\[ \text{CAROUGE-N}(s) = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]
+\[ \text{CAROUGE-N}(s) = \frac1n \sum_{i=1}^n \frac{1 - \operatorname*{min}_j ||s_i - c_j||}{k} \]
 
@@
 
+Using the same example as in the section \ref{sec:rouge} we can see that CAROUGE score of a decent abstractive summary will be greater than 0.
+
+\[ r = \text{"The great paper"} \]
+\[ s = \text{"A wonderful article"} \]
+\[ \text{ROUGE}(s) = 0 \]
+\[ \text{CAROUGE}(s) = 0.8956 \]
+
 \section{Experiments and results}
 
-We have tried different methods of text summarization, both extractive (TextRank, TF-IDF) and abstractive (Seq2Seq, SeqGAN).
+We have tried different methods of text summarization, both extractive (TextRank, RAKE) and abstractive (Seq2Seq, SeqGAN).
+
+\subsection{RAKE}
+
+Rapid Automatic Keyword Extraction algorithm (RAKE)\cite{rose-10} is a keyword extraction algorithm which tries to determine key phrases in a body of text by analyzing the frequency of word appearance and its co-occurance with other words in the text.
+Its main advantages include  time efﬁciency, operating on individual documents.
+It can be easily applied to new domains and multiple types of documents.
+RAKE is very sensitive to unclean data, as it relies on word frequency.
+
+\begin{table}[H]
+\caption{Example of an abstract generated by RAKE}
+
+\begin{center}
+\begin{tabular}{|p{0.25\linewidth}|p{0.67\linewidth}|}
+\hline
+\textbf{Title} & The Multivariate Generalised von Mises distribution: Inference and  applications \\
+\hline
+\textbf{Real abstract} & ...Previously proposed multivariate circular distributions are shown to be special cases of this construction.
+Second, we introduce a new probabilistic model for circular regression, that is inspired by Gaussian Processes, and a method for probabilistic principal component analysis with circular hidden variables...
+\\
+\hline
+\textbf{\makecell[l]{Generated \\ abstract}} & ...many data modelling problems since higher order generalised von mises distributions model circular variables using distributional assumptions probabilistic principal component analysis ppca proposed resulting distribution inherits desirable characteristics paper makes three technical contribu tions multivariate generalised...
+\\
+\hline
+\end{tabular}
+\end{center}
+\end{table}
 
@@
 Scores were calculated on the basis of ROUGE score.
+Unlike RAKE which operates n-grams, TextRank generates summaries using whole sentences.
+For that reason the generated summaries are more readable.
 
 \begin{table}[H]
-\caption{Example of an abstract generated by our model}
+\caption{Example of an abstract generated by TextRank}
 
@@
 
+In the table below you can see the results of our experiments represented by mean scores over all 2000 papers from our dataset.
+
 \begin{table}[H]
@@
 
+% \begin{center}
+% \begin{tabular}{|l|c|c|c|c|}
+% \hline
+% \textbf{Model} & \textbf{ROUGE-1} & \textbf{ROUGE-2} & \textbf{ROUGE-L} & \textbf{CAROUGE-1} \\
+% \hline
+% TextRank & 18.04 & 4.10 & 10.89 & 0 \\
+% RAKE & 8.93 & 1.54 & 7.54 & 0 \\
+% Human & 0 & 0 & 0 & 0 \\
+% \hline
+% \end{tabular}
+% \end{center}
+% \end{table}
+
 \begin{center}
-\begin{tabular}{|l|c|c|c|}
+\begin{tabular}{|l|c|c|c|c|}
 \hline
-\textbf{Model} & \textbf{ROUGE-1} & \textbf{ROUGE-2} & \textbf{ROUGE-L} \\
+\textbf{Model} & \textbf{ROUGE-1} & \textbf{ROUGE-2} & \textbf{CAROUGE-1} \\
 \hline
-TextRank & 18.04 & 4.10 & 10.89 \\
-LSTM & 0 & 0 & 0 \\
-SeqGAN & 0 & 0 & 0 \\
+TextRank & 18.04 & 4.10 & 0 \\
+RAKE & 8.93 & 1.54 & 0 \\
+Human & 0 & 0 & 0 \\
 \hline
@@
 \end{table}
-
-% \subsection{Timeframes}
-
-% \paragraph{Deliverables for the $1^{st}$ evaluation}
-% \begin{itemize}
-% \item Dataset of papers collected from arXiv
-% \item Results of feature extraction
-% \item Implementations of the baseline state-of-the-art model and its application to our dataset
-% \end{itemize}
-
-% \paragraph{Deliverables for the $2^{nd}$ (final) evaluation}
-% \begin{itemize}
-% \item Implementation of several discrete GAN models
-% \item Evaluation of the created models on our dataset
-% \item Paper describing the results of our research
-% \end{itemize}
 

### 2018-06-10 src/models/RAKE/summarize_rake_abstract_title.py
abstracts summarized to titles

@@ -18,23 +18,18 @@ def summarize_doc(content, length):
 dataset = pd.read_csv('../../../data/papers-2K.csv')
 rake_res = pd.DataFrame(dataset['id'])
 rake_res['ROUGE2_f_unfilter'], rake_res['ROUGE1_f_unfilter'], rake_res['ROUGE1_p_unfilter'], rake_res['ROUGE2_p_unfilter'] = None, None, None, None
-rake_res['Summary'], rake_res['ROUGEl_p_unfilter'], rake_res['ROUGEl_f_unfilter'] = None, None, None
+rake_res['Title'], rake_res['ROUGEl_p_unfilter'], rake_res['ROUGEl_f_unfilter'] = None, None, None
+print(dataset.columns)
 
 for index, paper in dataset.iterrows():
     try:
-        content = paper['text']
-        if len(content) < len(paper['abstract']) * 3:
-            print("Too small text for paper", paper['id'], index)
-            raise ValueError
-        # ratio = round(len(paper['abstract'])/len(content), 3)
-        num_words = len(paper['abstract'].split(' '))
-        sum_text  = summarize_doc(content, num_words)
-
-        abstract = paper['abstract'].split()
+        content = paper['abstract']
+        num = len(paper['title'].split(' '))
+        sum_text = summarize_doc(content, num)
 
         rouge_unfilter = Rouge()
-        rouge_score_unfilter = rouge_unfilter.get_scores(' '.join(sum_text), paper['abstract'])
-        rake_res['Summary'].iloc[index] = ' '.join(sum_text)
+        rouge_score_unfilter = rouge_unfilter.get_scores(' '.join(sum_text), paper['title'])
+        rake_res['Title'].iloc[index] = ' '.join(sum_text)
         rake_res['ROUGE2_f_unfilter'].iloc[index] = rouge_score_unfilter[0]['rouge-2']['f']
         rake_res['ROUGE1_f_unfilter'].iloc[index] = rouge_score_unfilter[0]['rouge-1']['f']
         rake_res['ROUGEl_f_unfilter'].iloc[index] = rouge_score_unfilter[0]['rouge-l']['f']
@@ -44,4 +39,4 @@ for index, paper in dataset.iterrows():
         pass
 
 print(rake_res.head(5))
-rake_res.to_csv('rake_scores.csv', index=False)
+rake_res.to_csv('rake_scores_title.csv', index=False)

### 2018-06-10 src/models/TextRank/summarize_textrank_title.py

@@ -1,0 +1,49 @@
+from gensim.summarization.summarizer import summarize
+from nltk.corpus import stopwords
+from nltk.tokenize import RegexpTokenizer
+from rouge import Rouge
+import pandas as pd
+
+
+def summarize_doc(content, len_words):
+    """
+    Summarization of one document using TextRank-based model from gensim library.
+    :param content: text in string format
+    :param len_words: number of words to 'generate', output summary size
+    :return: summary and list of cleaned words from summary
+    """
+    summarized = summarize(content,  word_count=len_words)
+    words = summarized.split(' ')
+    tokenizer = RegexpTokenizer(r'\w+')
+    filtered_words = [word for word in words if word not in stopwords.words('english')]
+    filtered_words = tokenizer.tokenize(' '.join(filtered_words))
+    return summarized, filtered_words
+
+dataset = pd.read_csv('../../../data/papers-2K.csv')
+testrank_res = pd.DataFrame(dataset['id'])
+testrank_res['BLEU_unfilter'], testrank_res['ROUGE2_f_unfilter'], testrank_res['ROUGE1_f_unfilter'], testrank_res['ROUGE1_p_unfilter'], testrank_res['ROUGE2_p_unfilter'] = None, None, None, None, None
+testrank_res['Summary'] = None
+testrank_res['ROUGEl_p_unfilter'],testrank_res['ROUGEl_f_unfilter'] = None, None
+
+for index, paper in dataset.iterrows():
+    try:
+        content = paper['abstract']
+
+        num_words = len(paper['title'].split(' '))
+        sum_text, filtered_words = summarize_doc(content, num_words)
+
+        rouge_unfilter = Rouge()
+        rouge_score_unfilter = rouge_unfilter.get_scores(sum_text, paper['title'])
+
+        # print(len(sum_text), len(paper['abstract']), len(' '.join(filtered_abstract)), len(' '.join(filtered_words)))
+        testrank_res['ROUGE2_f_unfilter'].iloc[index] = rouge_score_unfilter[0]['rouge-2']['f']
+        testrank_res['ROUGE1_f_unfilter'].iloc[index] = rouge_score_unfilter[0]['rouge-1']['f']
+        testrank_res['ROUGEl_f_unfilter'].iloc[index] = rouge_score_unfilter[0]['rouge-l']['f']
+        testrank_res['Summary'].iloc[index] = ' '.join(sum_text)
+
+        print("Iteration: ", index)
[…]

### 2018-06-10 src/models/seqgan-text-tensorflow/model.py

@@ -1,5 +1,5 @@
 """Utils for the TensorFlow model."""
-""" 
+"""
 This model on based on the work of Benjamin Bolte
 Source: https://github.com/carrotflakes/seqgan-text-tensorflow
 """

### 2018-06-10 paper/paper.tex
Updating the paper

@@
 
-\paragraph{Extractive text summarization}
-
-\subsection{Abstractive summarization}
+\paragraph{Extractive text summarization} identifies and extracts important words, phrases, or sentences from a document and puts them together as a summary.
+As a result, the produced summary is a subset of the words from original summary\cite{kumar-16}.
+Most work in the field of text summarization has been done around extractive summarization.
+Generally, it produces better results in terms of the amount of information preserved in a short summary.
 
 \paragraph{Abstractive text summarization} allows us to write summaries that are almost as good as those written by humans.
-It is closer to what humans do when they write text summaries, but also more complex.
-T
+Generally speaking, abstractive models perform worse than extractive ones.
+They are hard to train and often deviate too much from the original text.
+And since they try to describe the meaning of a text using different words, they preserve less information.
+Nevertheless, abstractive summarization is closer to what humans do when they write text summaries, and for that reason this is a very promissing AI topics.
 
@@
 
-To choose which words are important we can use an algorithm of extractive text summarization.
-We will use \textbf{term frequency-inverse document frequency} (tf-idf) as a measure of importance because of its simplicity and importance (according to \cite{kumar-16}, tf-idf is one of the universally used terminologies in extractive summarization).
+Deciding which words or sentences are important in a piece of text is part of the extractive summarization problem.
+Therefore, one way to choose $k$ important words would be to use part of a simple extractive model.
+For example, we could use tf-idf (term frequency-inverse document frequency) which would assign the highest scores to the words ($n$-grams) which are very frequent in the given document and very unfrequent in other documents.
+
+Another way of choosing important words would be to follow the assumption of ROUGE, according to which a good summary should be as close as possible to the human-created summaries.
+This means that we will compare generated summaries to the corresponding paper abstract (which are in fact author-created summaries).
 
@@
 
-In the table below you can see the results of our experiments represented by mean scores over all 2000 papers from our dataset.
+In the table below you can see the results of our experiments represented by mean scores of several models that were used to generate abstracts for same 2000 papers from our dataset given their text bodies.
 
@@
 \caption{Evaluating different models with ROUGE}
-
-% \begin{center}
-% \begin{tabular}{|l|c|c|c|c|}
-% \hline
-% \textbf{Model} & \textbf{ROUGE-1} & \textbf{ROUGE-2} & \textbf{ROUGE-L} & \textbf{CAROUGE-1} \\
-% \hline
-% TextRank & 18.04 & 4.10 & 10.89 & 0 \\
-% RAKE & 8.93 & 1.54 & 7.54 & 0 \\
-% Human & 0 & 0 & 0 & 0 \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \end{table}
 
@@
 \hline
-TextRank & 18.04 & 4.10 & 0 \\
-RAKE & 8.93 & 1.54 & 0 \\
-Human & 0 & 0 & 0 \\
+TextRank & 0.18 & 0.04 & 0.89 \\
+RAKE & 0.08 & 0.02 & 0.82 \\
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+
+We have also involved some human judges and asked them to come up with titles for 5 papers from our dataset, given their abstracts.
+
+\begin{table}[H]
+\caption{Evaluating different models with ROUGE}
+
+\begin{center}
+\begin{tabular}{|l|c|c|c|c|}
+\hline
+\textbf{Model} & \textbf{ROUGE-1} & \textbf{ROUGE-2} & \textbf{CAROUGE-1} \\
+\hline
+Human & 0.77 & 0.43 & 0 \\
 \hline
@@
 
-% We would like to express our gratitude to Anatolii Stehnii, Artem Chernodub, Maryana Romanyshyn, and Oksana Tkach for supporting us with their advices.
+% We would like to express our gratitude to Anatolii Stehnii, Artem Chernodub, and Maryana Romanyshyn for helping us with their advices.
 

### 2018-06-10 paper/paper.tex
Added CAROUGE values for human judges
Changed table captions
fixed grammar

@@
 
-In this work we overview recent advancements in the field of abstractive text summarization and discuss the use of deep learning models, especially Generative Adversarial Networks (GAN).
-We apply different models to our dataset of scientifix papers, acquired from arXiv, and evaluate them in terms of simplicity and performance.
+In this work, we overview recent advancements in the field of abstractive text summarization and discuss the use of deep learning models, especially Generative Adversarial Networks (GAN).
+We apply different models to our dataset of scientific papers, acquired from arXiv, and evaluate them in terms of simplicity and performance.
 
@@
 And since they try to describe the meaning of a text using different words, they preserve less information.
-Nevertheless, abstractive summarization is closer to what humans do when they write text summaries, and for that reason this is a very promissing AI topics.
+Nevertheless, abstractive summarization is closer to what humans do when they write text summaries, and for that reason, this is a very promising AI topics.
 
@@
 
-In this study we focus on abstractive text summarization.
+In this study, we focus on abstractive text summarization.
 We do a brief overview of the related work that has been done in this field.
-Then we proceed to discussing different models for statistical and deep summarization.
+Then we proceed to discuss different models for statistical and deep summarization.
 Then we present our dataset of scientific papers collected from arXiv and compare the performance of different models on this dataset.
@@
 This September Li et al.
-\cite{li-cohn-17} described their submission to the sentiment analysis sub-task of ?Build It, Break It: The Language Edition (BIBI)?
-where they successfully apply generative approach to the problem of sentiment analysis.
+\cite{li-cohn-17} described their submission to the sentiment analysis sub-task of Build It, Break It: The Language Edition (BIBI) where they successfully apply a generative approach to the problem of sentiment analysis.
 
@@
 
-In contrast Zhang et al.\cite{zhang-17} don't use reinforcement learning but rather introduce TextGAN with an LSTM-based generator and kernelized discrepancy metric.
+In contrast, Zhang et al.\cite{zhang-17} don't use reinforcement learning but rather introduce TextGAN with an LSTM-based generator and kernelized discrepancy metric.
 
@@
 
-\paragraph{Structure of the data} Each paper on arXiv has a unique identifier (for eample: 1801.01587).
+\paragraph{Structure of the data} Each paper on arXiv has a unique identifier (for example: 1801.01587).
 It can be used to extract any data that is available and related to that paper, including its metadata and full text as PDF.
@@
 
-Our script\footnote{Code and instructions for collecting the data is available in our repository: \url{https://github.com/Carouge/TextSummarization}} can be used to collect more data, but for our problem a set of 2000 papers from one category is enough.
-For example, DUC (Document Understanding Conference) dataset which is among the most commonly used in the feld of text summarization has 30 sets with approximately 10 documents each\footnote{\url{https://www-nlpir.nist.gov/projects/duc/guidelines/2001.html}}.
+Our script\footnote{Code and instructions for collecting the data are available in our repository: \url{https://github.com/Carouge/TextSummarization}} can be used to collect more data, but for our problem, a set of 2000 papers from one category is enough.
+For example, DUC (Document Understanding Conference) dataset which is among the most commonly used in the field of text summarization has 30 sets with approximately 10 documents each\footnote{\url{https://www-nlpir.nist.gov/projects/duc/guidelines/2001.html}}.
 
 \paragraph{Cleaning the text} We collected our data as PDF files and parsed them to extract the raw text.
-This produced a huge amount of uniterpretable UTF-8 characters from mathematical expressions.
+This produced a huge amount of uninterpretable UTF-8 characters from mathematical expressions.
 After removing those extra characters.
 
-We wanted to remove everething that is not a known English word, but that would filter out words like "GAN", "backprop" etc.
-as most standard corpuses of words, such as nltk.corpus, don't include specialized scientific terminology.
-So we filtered the words using manually created rules based on features like word length and frequence of vowels.
+We wanted to remove everything that is not a known English word, but that would filter out words like "GAN", "backprop" etc.
+as most standard corpora of words, such as nltk.corpus, don't include specialized scientific terminology.
+So we filtered the words using manually created rules based on features like word length and frequency of vowels.
 This leaves some noise behind, but it will not affect our models.
@@
 
-Three main classes of models that are used for text summarization task are statistical frequency computation models (TFIDF etc.), graph methods (TextRank, LexRank etc.) and machine learning approach.
+Three main classes of models that are used for a text summarization task are statistical frequency computation models (TFIDF etc.), graph methods (TextRank, LexRank etc.) and machine learning approach.
 
@@
 The weights on these edges represent similarity between words or sentences in the whole text.
-While proving to have better results than simple frequency-based methods, graph models are still bounded by the absence of lexic understanding and ability to perform extractive summary only.
+While proving to have better results than simple frequency-based methods, graph models are still bounded by the absence of lexical understanding and ability to perform extractive summary only.
 
@@
 Evaluating a summary is a difficult task because there is no such thing as a single summary that would be ideal for a given document.
-In most cases even human evaluators can not agree on which of the given summaries is better\cite{das-7}.
+In most cases, even human evaluators cannot agree on which of the given summaries is better\cite{das-7}.
 Unlike other NLP problems, such as translation or parsing, when it comes to text summarization we can not clearly define what makes a summary good or bad.
@@
 \item assume that a good summary would be close to some \textit{ideal} summary manually created by humans
-\item assume that the goodness of summary can be measured as the ammount of important information it contains (this assumption can be infered from the definition of text summarization).
+\item assume that the goodness of summary can be measured as the amount of important information it contains (this assumption can be inferred from the definition of text summarization).
 \end{enumerate}
 
-In the following sections we briefly describe some of the commonly used metrics for text summarization that is based on the first assumption and propose our own metric that is based on second one (in fact, we will show that the proposed metric can be formulated in a different way to work with the first assumption).
+In the following sections, we briefly describe some of the commonly used metrics for text summarization that is based on the first assumption and propose our own metric that is based on second one (in fact, we will show that the proposed metric can be formulated in a different way to work with the first assumption).
 
@@
 
-The most widely used score for evaluating text summarizations is ROUGE (Recall-Oriented Understudy for Gisting Evaluation) inroduced by Chin-Yew Lin in 2004\cite{lin-4}.
+The most widely used score for evaluating text summarizations is ROUGE (Recall-Oriented Understudy for Gisting Evaluation) introduced by Chin-Yew Lin in 2004\cite{lin-4}.
 
@@
 ROUGE works well for extractive text summarization.
-But if we need to evaluate the generated summary which contains different words from the ones that occured in paper, the score will always be small because, even though the new words can be close to the expected ones, two summaries don't overlap in terms of word equality.
+But if we need to evaluate the generated summary which contains different words from the ones that occurred in the paper, the score will always be small because, even though the new words can be close to the expected ones, two summaries don't overlap in terms of word equality.
 
@@
 
-We propose a metric that uses word embeddings to evaluate summaries based on their semmantic distance to the space of good summaries.
+We propose a metric that uses word embeddings to evaluate summaries based on their semantic distance to the space of good summaries.
 Our assumption is that a good summary of a document contains words that are semantically close to the most important words or n-grams in that document.
@@
 
-The metric we propose is in fact a continuous version of ROUGE-N.
-Instead of testing the equality of n-grams in the compared summaries we use the continuous measure of semmantic distance between those n-grams.
+The metric we propose is, in fact, a continuous version of ROUGE-N.
+Instead of testing the equality of n-grams in the compared summaries we use the continuous measure of semantic distance between those n-grams.
 
@@
 
-Rapid Automatic Keyword Extraction algorithm (RAKE)\cite{rose-10} is a keyword extraction algorithm which tries to determine key phrases in a body of text by analyzing the frequency of word appearance and its co-occurance with other words in the text.
+Rapid Automatic Keyword Extraction algorithm (RAKE)\cite{rose-10} is a keyword extraction algorithm which tries to determine key phrases in a body of text by analyzing the frequency of word appearance and its co-occurrence with other words in the text.
 Its main advantages include time efﬁciency, operating on individual documents.
@@
 \subsection{TextRank}
-In this research we used a basic model TextRank as a baseline for comparison.
+In this research, we used a basic model TextRank as a baseline for comparison.
 This is a graph method, influenced by PageRank algorithm, that represents the documents as a connected graph\cite{mihalcea-4}.
@@
 Unlike RAKE which operates n-grams, TextRank generates summaries using whole sentences.
-For that reason the generated summaries are more readable.
+For that reason, the generated summaries are more readable.
 
@@
 \hline
-\textbf{Real abstract} & ...for each player, we predict the probability of churning as function of time, which permits to distinguish various levels of loyalty profiles ...
+\textbf{Real abstract} & ...for each player, we predict the probability of churning as the function of time, which permits to distinguish various levels of loyalty profiles ...
 Our results show that churn prediction by survival ensembles significantly improves the accuracy and robustness of traditional analyses, like Cox regression...
@@
 
-After some training our model was able to generate meaningful titles for most abstracts. Take a look at this example:
+After some training, our model was able to generate meaningful titles for most abstracts. Take a look at this example:
 
@@
 \hline
-Human & 0.77 & 0.43 & 0 \\
+Human & 0.77 & 0.43 & 0.98 \\
 \hline
@@
 
-In this paper we demonstrated how Generative Adversarial Networks can be used for abstractive text summarization.
+In this paper, we demonstrated how Generative Adversarial Networks can be used for abstractive text summarization.
 
@@
 
-% We would like to express our gratitude to Anatolii Stehnii, Artem Chernodub, and Maryana Romanyshyn for helping us with their advices.
+% We would like to express our gratitude to Anatolii Stehnii, Artem Chernodub, and Maryana Romanyshyn for helping us with their pieces of advice.
 

### 2018-06-10 paper/paper.tex
Updated the related work

--- 2018-06-10 paper/paper.tex
@@
 
-Allahyari et al.\cite{allahyari-17} make a survey of the most successful text summarization techniques as of July 2017.
+Das et al. made a survey of the most successful text summarization techniques as of the year 2007\cite{das-7}. Simmilar survey was made 10 years later by Allahyari et al\cite{allahyari-17}.
 
-This September Li et al.
-\cite{li-cohn-17} described their submission to the sentiment analysis sub-task of ?Build It, Break It: The Language Edition (BIBI)?
-where they successfully apply generative approach to the problem of sentiment analysis.
+ROUGE - the most widely used metric for text summarization was presented by Chin-Yew Lin in July 2004\cite{lin-4}.
+The metric developed by us is greatly influenced by the the work of this author.
+Great overview of existing evaluation metrics was also done in \cite{das-7} and \cite{allahyari-17}.
 
-In their paper \textit{Generative Adversarial Network for Abstractive Text Summarization} Liu et al.\cite{liu-17} built an adversarial model that achieved competitive ROUGE scores with the state-of-the-art methods on CNN/Daily Mail dataset.
-They compare the performance of their approach with three methods, including the abstractive model, the pointer-generator coverage networks, and the abstractive deep reinforced model.
-
-In contrast Zhang et al.\cite{zhang-17} don't use reinforcement learning but rather introduce TextGAN with an LSTM-based generator and kernelized discrepancy metric.
+Fedus, Goodfellow, and Dai\cite{fedus-18} wrote an amazing paper about their application of generative adversarial networks to the problem of filling the gaps in text.
+However, as we show in section \ref{sec:ml}, this approach can not be easily applied to our problem.
 
@@
 \subsection{Machine learning approach}
+\label{sec:ml}
 
@@
 However, in their latest paper Fedus, Goodfellow, and Dai\cite{fedus-18} overcome this problem by using reinforcement learning to train the generator while the discriminator is still trained via maximum likelihood and stochastic gradient descent, and use it to fill the gaps in the text.
+This is an amazing result that can become an inspiration for others to develop GAN-based solutions for the problems of text sumarization.
+Nevertheless, summarization is way more complex than the problem of filling the gaps, and therefore, to our knowledge, there are no successful examples of applying adversarial networs to problems similar to ours.
+We ourselves have tried this new approach, but failed to produce good results.
 
@@
 Rapid Automatic Keyword Extraction algorithm (RAKE)\cite{rose-10} is a keyword extraction algorithm which tries to determine key phrases in a body of text by analyzing the frequency of word appearance and its co-occurance with other words in the text.
-Its main advantages include  time efﬁciency, operating on individual documents.
+Its main advantages include time efficiency, operating on individual documents.
 It can be easily applied to new domains and multiple types of documents.
@@
 \section{Evaluating results}
+\label{sec:results}
 
@@
 \begin{table}[H]
-\caption{Evaluating different models with ROUGE}
+\caption{Evaluating summarization algorithms}
 
@@
 \hline
+RAKE & 0.08 & 0.02 & 0.82 \\
 TextRank & 0.18 & 0.04 & 0.89 \\
-RAKE & 0.08 & 0.02 & 0.82 \\
 \hline
@@
 \begin{table}[H]
-\caption{Evaluating different models with ROUGE}
+\caption{Evaluating human judges}
 
@@
 
+As we have seen in section \ref{sec:results}, both ROUGE and CAROUGE metrics give very high scores to human-created summaries, and much lower scores for the summaries produced by algorithms.
+However, consider the fact that the base assumption of ROUGE takes human judgement as the ground truth
+
 % \section*{Acknowledgements}

### 2018-06-10 paper/paper.tex
Uploading the almost-final version of a paper

@@
 
-In this work we overview recent advancements in the field of abstractive text summarization and discuss the use of deep learning models, especially Generative Adversarial Networks (GAN).
-We apply different models to our dataset of scientifix papers, acquired from arXiv, and evaluate them in terms of simplicity and performance.
+Summarization of scientific papers is a unique case of text summarization which allows us to use abstracts as human-created labels for our dataset because they are the summaries written by the authors.
+This allows us to collect great amounts of labeled data for our models to learn from.
 
-We propose our own metric based on word-embeddings, which we believe will be more suitable for evaluation of abstractive summaries.
+In this work, we overview different approaches to text summarization and compare their results with different evaluation metrics.
+We demonstrate the downsides of ROUGE, the most commonly used summarization metric and introduce our own metric called CAROUGE, which gives more accurate scores for abstractive summaries.
+
+We also present our new dataset of 2000 scientific papers collected from arXiv.
+All experiments, described in this paper are performed on the data from our dataset, except for the final stage of our project where we involve 5 human judges to do a manual summarization of several papers from the dataset.
 
@@
 
-\subsection{Structure of the paper}
+% \subsection{Structure of the paper}
 
-In this study we focus on abstractive text summarization.
+% In this study we focus on abstractive text summarization.
 We do a brief overview of the related work that has been done in this field.
@@
 
-In the following sections we briefly describe some of the commonly used metrics for text summarization that is based on the first assumption and propose our own metric that is based on second one (in fact, we will show that the proposed metric can be formulated in a different way to work with the first assumption).
+In the following sections we describe one commonly used summarization metric that is based on the first assumption and propose our own metric that is based on second one (we will show that the proposed metric can be formulated in a different way to work with the first assumption).
 
@@
 
-\[ \text{ROUGE-N}(s) = \frac{\sum_{r \in R} \langle \Phi_n(r), \Phi_n(s) \rangle}{\sum_{r \in R} \langle \Phi_n(r), \Phi_n(r) \rangle} \]
+\[ \text{ROUGE-N}(s) = \frac{\sum_{r \in R} \langle \Phi_n(r), \Phi_n(s) \rangle}{\sum_{r \in R} \langle \Phi_n(r), \Phi_n(r) \rangle} \].
 
-\[ \text{ROUGE-L}(s) = \frac{(1 + \beta^2) R_{LCS} P_{LCS}}{R_{LCS} + \beta^2 P_{LCS}} \]
+Here $\Phi_n(d)$ is a binary vector representing the $n$-grams contained in document $d$, $s$ is the generated summary and $r$ is the human-created summary.
+In simple terms, ROUGE-N is a fraction $q/k$, where $q$ is the number of $n$-grams that are present in both $s$ and $r$, and $k$ is the total number of $n$-grams in $r$.
 
@@
 
-In this paper we demonstrated how Generative Adversarial Networks can be used for abstractive text summarization.
+We have discussed different approaches to scientific text summarization and evaluated them with both ROUGE and CAROUGE (Continuous Abstractive ROUGE) - a new metric proposed by us that produces more accurate scores of abstractive summaries thanks to its continuous nature.
 
 As we have seen in section \ref{sec:results}, both ROUGE and CAROUGE metrics give very high scores to human-created summaries, and much lower scores for the summaries produced by algorithms.
-However, consider the fact that the base assumption of ROUGE takes human judgement as the ground truth
+However, considering the fact that ROUGE assumes human-judgement to be perfect, the score of 0.43 is way too low.
+As we explained in section \ref{sec:rouge}, this happens because human judgement is abstractive by its nature, and ROUGE score words best on extractive summaries.
+This problem is fixed by our metric, which gives the score of 0.98 on the same data.
 

### 2018-06-10 paper/paper.tex
Added the acknowledgements

@@
 
-We have discussed different approaches to scientific text summarization and evaluated them with both ROUGE and CAROUGE (Continuous Abstractive ROUGE) - a new metric proposed by us that produces more accurate scores of abstractive summaries thanks to its continuous nature.
+We have discussed different approaches to scientific text summarization and evaluated them with both ROUGE and CAROUGE (Continuous Abstractive ROUGE) - a new metric proposed by us that uses word embeddings to produce more accurate scores of abstractive summaries.
 
 As we have seen in section \ref{sec:results}, both ROUGE and CAROUGE metrics give very high scores to human-created summaries, and much lower scores for the summaries produced by algorithms.
-However, considering the fact that ROUGE assumes human-judgement to be perfect, the score of 0.43 is way too low.
+However, considering the fact that ROUGE assumes human-judgement to be perfect, the score of 0.77 is way too low.
 As we explained in section \ref{sec:rouge}, this happens because human judgement is abstractive by its nature, and ROUGE score words best on extractive summaries.
@@
 
-% \section*{Acknowledgements}
+\section*{Acknowledgements}
 
-% We would like to express our gratitude to Anatolii Stehnii, Artem Chernodub, and Maryana Romanyshyn for helping us with their advices.
+We would like to express our gratitude to Anatolii Stehnii, Artem Chernodub, and Maryana Romanyshyn for helping us with their advices.
+Also, we are very grateful to Rostyslav Zatserkovnyi, Anton Tarasov, Ivan Ilnytskyi, Taras Panychok, and Bohdan Petryshak for providing their manually created summaries of some papers from our dataset.
 

### 2018-06-10 paper/paper.tex
Changed the title

@@
 
-\title{Automatic Summarization of Scientific Texts}
+\title{CAROUGE - the new metric for text summarization}
 
@@
 \paragraph{Cleaning the text} We collected our data as PDF files and parsed them to extract the raw text.
-This produced a huge amount of uniterpretable UTF-8 characters from mathematical expressions.
+This produced a huge amount of uninterpretable UTF-8 characters from mathematical expressions.
 After removing those extra characters.
 
-We wanted to remove everething that is not a known English word, but that would filter out words like "GAN", "backprop" etc.
-as most standard corpuses of words, such as nltk.corpus, don't include specialized scientific terminology.
-So we filtered the words using manually created rules based on features like word length and frequence of vowels.
+We wanted to remove everything that is not a known English word, but that would filter out words like "GAN", "backprop" etc.
+as most standard corpora of words, such as nltk.corpus, don't include specialized scientific terminology.
+So we filtered the words using manually created rules based on features like word length and frequency of vowels.
 This leaves some noise behind, but it will not affect our models.
@@
 \item assume that a good summary would be close to some \textit{ideal} summary manually created by humans
-\item assume that the goodness of summary can be measured as the ammount of important information it contains (this assumption can be infered from the definition of text summarization).
+\item assume that the goodness of summary can be measured as the amount of important information it contains (this assumption can be inferred from the definition of text summarization).
 \end{enumerate}
@@
 ROUGE works well for extractive text summarization.
-But if we need to evaluate the generated summary which contains different words from the ones that occured in paper, the score will always be small because, even though the new words can be close to the expected ones, two summaries don't overlap in terms of word equality.
+But if we need to evaluate the generated summary which contains different words from the ones that occurred in paper, the score will always be small because, even though the new words can be close to the expected ones, two summaries don't overlap in terms of word equality.
 
@@
 The metric we propose is in fact a continuous version of ROUGE-N.
-Instead of testing the equality of n-grams in the compared summaries we use the continuous measure of semmantic distance between those n-grams.
+Instead of testing the equality of n-grams in the compared summaries we use the continuous measure of semantic distance between those n-grams.
 
@@
 
-Rapid Automatic Keyword Extraction algorithm (RAKE)\cite{rose-10} is a keyword extraction algorithm which tries to determine key phrases in a body of text by analyzing the frequency of word appearance and its co-occurance with other words in the text.
+Rapid Automatic Keyword Extraction algorithm (RAKE)\cite{rose-10} is a keyword extraction algorithm which tries to determine key phrases in a body of text by analyzing the frequency of word appearance and its co-occurrance with other words in the text.
 Its main advantages include time efficiency, operating on individual documents.
@@
 
-We would like to express our gratitude to Anatolii Stehnii, Artem Chernodub, and Maryana Romanyshyn for helping us with their advices.
+We would like to express our gratitude to Anatolii Stehnii, Artem Chernodub, and Maryana Romanyshyn for helping us with their valuable pieces of advice.
 Also, we are very grateful to Rostyslav Zatserkovnyi, Anton Tarasov, Ivan Ilnytskyi, Taras Panychok, and Bohdan Petryshak for providing their manually created summaries of some papers from our dataset.
